---
title: "Capture data Table 1"
output: html_notebook
---


```{r echo=FALSE, message=FALSE}
rm(list=ls())
ifelse(Sys.info()[1] == 'Linux',
       source('~/Documents/R/tools/TomosFunctions.R'),
       source('~/R/tools/TomosFunctions.R'))

#library(readxl)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
```

This notebook creates Table 1. It brings in the file IDvsUDs_2018-11-01.csv, which was created by HR_analylsis_GPS_LC_newtags.Rmd, which also used another file all_sample_summary_size_2018-07-24.csv. See each of these files for details. 

```{r}

data1 <- read.csv(file = "data/IDvsUDs_2019-11-06.csv")

data1 %>% dplyr::select(ID.f, Capture_Date, n.days, n.relocations,
                 n.relocations.all, n.day, n.day.all,
                 n.night, n.night.all, Sex, Mass_kg, SCL_cm,
                 period) -> data2

head(data2)
```

Then compute some statistics that were needed in the text.

```{r}
mean(data2$SCL_cm)
SE(data2$SCL_cm)
mean(data2$Mass_kg)
SE(data2$Mass_kg)
mean(data2$n.days)
SE(data2$n.days)
```

Split statistics into pre and post periods:
```{r}
data2 %>% mutate(period.f = as.factor(period)) %>%
  group_by(period.f) %>% summarise(mean.n.days = mean(n.days),
                                   SE.n.days = SE(n.days),
                                   mean.n.relocations = mean(n.relocations),
                                   SE.n.relocations = SE(n.relocations),
                                   mean.n.relocations.all = mean(n.relocations.all),
                                   SE.n.relocations.all = SE(n.relocations.all),
                                   mean.n.day = mean(n.day),
                                   SE.n.day = SE(n.day),
                                   mean.n.day.all = mean(n.day.all),
                                   SE.n.day.all = SE(n.day.all),
                                   mean.n.night = mean(n.night),
                                   SE.n.night = SE(n.night),
                                   mean.n.night.all = mean(n.night.all),
                                   SE.n.night.all = SE(n.night.all),
                                   mean.Mass = mean(Mass_kg),
                                   SE.Mass = SE(Mass_kg),
                                   mean.SCL = mean(SCL_cm),
                                   SE.SCL = SE(SCL_cm)) -> data2.by.period
```


Then do comparisons between pre and post for SCL, Mass, and transmission days.

```{r}
fit.SCL <- lm(SCL_cm ~ period, data = data2)
summary(fit.SCL)
```

```{r}
fit.Mass <- lm(Mass_kg ~ period, data = data2)
summary(fit.Mass)
```

```{r}
fit.days <- lm(n.days ~ period, data = data2)
summary(fit.days)
```



