---
title: "Extract statistics for ms revision"
output: html_notebook
---

This document extracts necessary statistics for the revision of the manuscript

```{r}
rm(list = ls())

library(dplyr)
library(adehabitatHR)
library(rgdal)
library(leaflet) 
library(ggplot2)
library(lubridate)
library(tidyverse)
library(ggridges)

source("HR_analysis_fcns.R")

# internet <- F #TRUE
save.fig <- T

# Minimum number of relocations per individual to be included in HR analysis
min_n <- 50
#N.end <- 32.69   # approx Coronado bridge
N.end <- 32.66 # changed from 32.69 because 152314 had a gap in data points between ~32.65 and ~32.66 - seems like there was a different behavior south and north of 32.66

grid <- 1000
extent <- 1

#source("HR_analysis_fcns.R")
tagprj <- readOGR(dsn = "Tag_065_UTMzone11n", 
                  layer = "tag_065_project")
tagproj <- proj4string(tagprj)

all.data <- readRDS(file = "RData/PreVsPost_DayNight_Dec2019.RDS")
```

Then, pull out statistics in the order that they are used in the manuscript. 

To find out the proportion of accepted locations for GPS, we need to pull out files with _inout.csv extensions. 

First, day and night are combined. pre.n and post.n contain four columns:

1. ArgosID

2. the number of data points after deciding inside or outside SDB (all)

3. the number of data points excluding those with residual values > 35.0, outside SDB, and north of N.end (32.66 as of 16 Dec 2019) (filtered)

4. the number of data points after splitting into 4-hr blocks and taking one from each block

```{r}
pre.all <- read.csv("data/Pre_GPS_all.csv")
post.all <- read.csv("data/Post_GPS_all.csv")

pre.IDs <- unique(pre.all$ArgosID)
post.IDs <- unique(post.all$ArgosID)
all.IDs <- c(pre.IDs, post.IDs)

post.n <- pre.n <- data.frame(ArgosID = NA, all = NA, filtered = NA, final = NA)
k <- 1
for (k in 1:length(pre.IDs)){
  filename <- paste0("data/files_Oct2019_withNewTags/pre/", 
                     pre.IDs[k], "_inout.csv")
  filename1 <- paste0("data/files_Oct2019_withNewTags/pre/", 
                      pre.IDs[k], "_inside_DayNight_4hrs_GPS.csv")
  dat.all <- read.csv(file = filename) %>% filter(Message_Type == "GPS")
  dat.all %>% filter(Lat1 < N.end) %>% 
    filter(Residual <= 35) %>%
    filter(inside == 1) -> dat.filtered
  dat.final <- read.csv(file = filename1)

  pre.n[k, ] <- c(pre.IDs[k], nrow(dat.all), nrow(dat.filtered), nrow(dat.final))

}

pre.n$pre0post1 <- 0

k <- 1
for (k in 1:length(post.IDs)){
  # these are "new" tags
  if (post.IDs[k] <= 152323 & post.IDs[k] >= 151375 ){
    filename <- paste0("data/files_Oct2019_withNewTags/new/", 
                       post.IDs[k], "_inout.csv")
    filename1 <- paste0("data/files_Oct2019_withNewTags/new/", 
                        post.IDs[k], "_inside_DayNight_4hrs_GPS.csv")
    
  } else {
    filename <- paste0("data/files_Oct2019_withNewTags/post/", 
                       post.IDs[k], "_inout.csv")
    filename1 <- paste0("data/files_Oct2019_withNewTags/post/", 
                        post.IDs[k], "_inside_DayNight_4hrs_GPS.csv")
    
  }
  
  dat.all <- read.csv(file = filename) %>% filter(Message_Type == "GPS")
  dat.all %>% filter(Lat1 < N.end) %>% 
    filter(Residual <= 35) %>%
    filter(inside == 1) -> dat.filtered
  
  dat.final <- read.csv(file = filename1)
  
  post.n[k, ] <- c(post.IDs[k], nrow(dat.all), nrow(dat.filtered), nrow(dat.final))
  
}

post.n$pre0post1 <- 1

all.n <- rbind(pre.n, post.n) %>%
  mutate(prop.filtered = filtered/all,
         prop.used = final/all)

all.prop <- sum(all.n$filtered)/sum(all.n$all)

min.prop <- min(all.n$prop.filtered)

used.prop <- sum(all.n$final)/sum(all.n$all)
min.used.prop <- min(all.n$prop.used)

# we want at least 50 data points.
all.n %>% filter(final > 49) -> used.n

lost.pre <- nrow(all.n[all.n$pre0post1 == 0,]) - nrow(used.n[used.n$pre0post1 == 0,])
lost.post <- nrow(all.n[all.n$pre0post1 == 1,]) - nrow(used.n[used.n$pre0post1 == 1,])


```

Combine these with the HR analyses output to make one dataframe. All these files were created in HR_analysis_GPS_LC_newtags_2019-10-31.Rmd. 

```{r}
pre.UD <- readRDS("RData/pre_GPS_UD_byID.rds")

post.UD <- readRDS("RData/post_GPS_UD_byID.rds")

UD.area <- rbind(pre.UD$area, post.UD$area) %>%
  mutate(ArgosID = ID) %>% 
  dplyr::select(-ID)

used.n %>% left_join(UD.area, by = "ArgosID") -> used.n.byID

```


UDs for day and night periods (same here - created in HR_analysis_GPS_LC_newtags_2019-10-31.Rmd)

```{r}

pre.UD.day <- readRDS("RData/pre_GPS_UD_day.rds")
pre.UD.night <- readRDS("RData/pre_GPS_UD_night.rds")


```



```{r}
pre.GPS.HR <- readRDS(file = "RData/pre_GPS_HR.rds")
```


