---
title: "R Notebook"
output: html_notebook
---

Analysis of HR vs. various covariates

```{r echo=FALSE}
rm(list = ls())

ifelse(Sys.info()[1] == 'Linux',
       source('~/Documents/R/tools/TomosFunctions.R'),
       source('~/R/tools/TomosFunctions.R'))

#library(readxl)
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(lme4)

source("HR_analysis_fcns.R")

```



First bring in the HR data:
```{r}
data1 <- read.csv(file = "data/IDvsUDs_2018-11-01.csv")
# all.data.frames <- readRDS(file = "RData/PreVsPost_DayNight.RDS")
# KD.eachID.pre.combined <- all.data.frames[[1]]
# KD.eachID.post.combined<- all.data.frames[[2]] 
# KD.eachID.pre.day <- all.data.frames[[3]]
# KD.eachID.pre.night <- all.data.frames[[4]]
# KD.eachID.post.day <- all.data.frames[[5]] 
# KD.eachID.post.night <- all.data.frames[[6]] 
# UD.post.95.latlon <- all.data.frames[[7]] 
# UD.post.50.latlon <- all.data.frames[[8]] 
# UD.pre.95.latlon <- all.data.frames[[9]] 
# UD.pre.50.latlon <- all.data.frames[[10]] 
# UD.pre.day.95.latlon <- all.data.frames[[11]] 
# UD.pre.day.50.latlon <- all.data.frames[[12]]
# UD.pre.night.95.latlon <- all.data.frames[[13]] 
# UD.pre.night.50.latlon <- all.data.frames[[14]] 
# UD.post.day.95.latlon <- all.data.frames[[15]]
# UD.post.day.50.latlon <- all.data.frames[[16]] 
# UD.post.night.95.latlon <- all.data.frames[[17]]
# UD.post.night.50.latlon <- all.data.frames[[18]]
# UD.pre.day.night.95.latlon <- all.data.frames[[19]]
# UD.pre.day.night.50.latlon <- all.data.frames[[20]]
# UD.post.day.night.95.latlon <- all.data.frames[[21]]
# UD.post.day.night.50.latlon <- all.data.frames[[22]]
head(data1)
```

Get the water temp data:
```{r echo=FALSE, message=FALSE}
tmp14.mean <- tmp7.mean <- vector(mode = "numeric", length = nrow(data1))
tmp14.min <- tmp7.min <- vector(mode = "numeric", length = nrow(data1))
tmp14.max <- tmp7.max <- vector(mode = "numeric", length = nrow(data1))
tmp14.sd <- tmp7.sd <- vector(mode = "numeric", length = nrow(data1))
tmp.mean <- tmp.min <- tmp.max <- tmp.sd <- vector(mode = "numeric", length = nrow(data1))

k <- 1
for (k in 1:nrow(data1)){
  date1 <- as.Date(data1$Capture_Date[k], format = "%m/%d/%Y")
  n.days <- round(data1$n.days[k])
  tmp.7 <- tmp.summary(date1 - days(7), date1)
  tmp.14 <- tmp.summary(date1 - days(14), date1)
  tmp.deploy <- tmp.summary(date1, date1 + days(n.days))
  
  tmp7.mean[k] <- tmp.7$mean
  tmp7.min[k] <- tmp.7$min
  tmp7.max[k] <- tmp.7$max
  tmp7.sd[k] <- tmp.7$SD
  
  tmp14.mean[k] <- tmp.14$mean
  tmp14.min[k] <- tmp.14$min
  tmp14.max[k] <- tmp.14$max
  tmp14.sd[k] <- tmp.14$SD

  tmp.mean[k] <- tmp.deploy$mean
  tmp.min[k] <- tmp.deploy$min
  tmp.max[k] <- tmp.deploy$max
  tmp.sd[k] <- tmp.deploy$SD
  
}

data1$tmp7.mean <- unlist(tmp7.mean)
data1$tmp7.min <- unlist(tmp7.min)
data1$tmp7.max <- unlist(tmp7.max)
data1$tmp7.sd <- unlist(tmp7.sd)

data1$tmp14.mean <- unlist(tmp14.mean)
data1$tmp14.min <- unlist(tmp14.min)
data1$tmp14.max <- unlist(tmp14.max)
data1$tmp14.sd <- unlist(tmp14.sd)

data1$tmp.mean <- unlist(tmp.mean)
data1$tmp.min <- unlist(tmp.min)
data1$tmp.max <- unlist(tmp.max)
data1$tmp.sd <- unlist(tmp.sd)

data1$month <- month(as.Date(data1$Capture_Date, format = "%m/%d/%Y"))

# data1 %>% mutate(sex.num = ifelse(Sex == "F", 1, 
#                                   ifelse(Sex == "M", 2, 3))) %>%
#   mutate(period.num = ifelse(period == "pre", 1, 2)) -> data1

# data2 is centered and scaled. 
data2 <- data.frame(scale(select_if(data1, is.numeric)) )
data2$sex <- data1$Sex
data2$period <- data1$period
```

Then use GLM to look at how they affected the HR:

```{r}

fit.1.50 <- lm(area.50 ~ n.days + Mass_kg + period + tmp14.mean + tmp14.min + tmp14.max + tmp14.sd,
            data = data1)
summary(fit.1.50)
```

```{r}
fit.2.50 <- lm(area.50 ~ n.days + Mass_kg + period + tmp7.mean + tmp7.min + tmp7.max + tmp7.sd,
            data = data1)
summary(fit.2.50)

```


```{r}
fit.3.50 <- lm(area.50 ~ n.days + Mass_kg + tmp7.mean + tmp7.min + tmp7.max + tmp7.sd,
            data = data1)
summary(fit.3.50)

```


```{r}
fit.1.95 <- lm(area.95 ~ n.days + Mass_kg + period + tmp14.mean + tmp14.min + tmp14.max + tmp14.sd,
            data = data1)
summary(fit.1.95)

```

```{r}
fit.2.95 <- lm(area.95 ~ n.days + Mass_kg + period + tmp7.mean + tmp7.min + tmp7.max + tmp7.sd,
            data = data1)
summary(fit.2.95)

```



Temperature during the deployments. 
```{r}
formula.1 <- formula(area.50 ~ n.days + Mass_kg + period + 
                       tmp.mean + tmp.min + tmp.max + 
                       tmp.sd + month)
fit.1 <- lm(formula.1,
            data = data2)
summary(fit.1)
```


Temperatures 14 days prior to the tag deployments.

```{r}

fit.14days <- lm(area.50 ~ n.days + Mass_kg + period + 
                   tmp14.mean + tmp14.min + tmp14.max + 
                   tmp14.sd + month,
                 data = data2)
summary(fit.14days)
```

Temperatures during 7 days prior to the deployment dates.

```{r}
fit.7days <- lm(area.50 ~ n.days + Mass_kg + period + tmp7.mean + 
                  tmp7.min + tmp7.max + tmp7.sd + month,
                data = data2)
summary(fit.7days)

```

Temperatures during deployments and UD during daytime.

```{r}

fit.1.day <- lm(area.day.50 ~ n.days + Mass_kg + period + 
                  tmp.mean + tmp.min + tmp.max + tmp.sd + month,
                data = data2)
summary(fit.1.day)
```

Tempereatures during 14 days prior to the deployment dates and 50% UDs during daytime. 

```{r}

fit.day.14days <- lm(area.day.50 ~ n.days + Mass_kg + period + 
                       tmp14.mean + tmp14.min + tmp14.max + tmp14.sd + month,
                     data = data2)
summary(fit.day.14days)
```

Tempereatures during 7 days prior to the deployment dates and 50% UDs during daytime. 


```{r}

fit.day.7days <- lm(area.day.50 ~ n.days + Mass_kg + period + tmp7.mean + 
                        tmp7.min + tmp7.max + tmp7.sd + month,
                      data = data2)
summary(fit.day.7days)
```

Temperatures during the deployment periods and 50% UDs during nighttime. 

```{r}

fit.1.night <- lm(area.night.50 ~ n.days + Mass_kg + period + 
                    tmp.mean + tmp.min + tmp.max + tmp.sd + month,
                  data = data2)
summary(fit.1.night)
```

Temperatures during 14 days prior to the deployment date and 50% UDs during nighttime. 

```{r}

fit.night.14days <- lm(area.night.50 ~ n.days + Mass_kg + period + 
                         tmp14.mean + tmp14.min + tmp14.max + tmp14.sd + month,
                       data = data2)
summary(fit.night.14days)
```

Temperatures during 7 days prior to the deployment date and 50% UDs during nighttime. 

```{r}

fit.night.7days <- lm(area.night.50 ~ n.days + Mass_kg + period + 
                         tmp7.mean + tmp7.min + tmp7.max + tmp7.sd + month,
                       data = data2)
summary(fit.night.7days)
```


Could there be non-linear relationships?

```{r}
library(mgcv)
gam.1 <- gam(area.50 ~ n.days + Mass_kg + period + 
               tmp.mean + tmp.min + tmp.max + tmp.sd + month,
            data = data2)
summary(gam.1)

```



```{r}
gam.day <- gam(area.day.50 ~ n.days + Mass_kg + period + 
                         tmp.mean + tmp.min + tmp.max + tmp.sd + month,
            data = data2)
summary(gam.day)

```

```{r}
gam.night <- gam(area.night.50 ~ n.days + Mass_kg + period + 
                   tmp.mean + tmp.min + tmp.max + tmp.sd + month,
            data = data2)
summary(gam.night)

```

