---
title: "R Notebook"
output: html_notebook
---

San Diego Bay Turtle Movement Analysis
Original R Code, JT Froeschke, December 29, 2015
Data modified from previous versions by SE Graham, June 2016, May 2018
Data modified from May 2018 by T EGuchi, July 2018

Filtered data utilize GPS, and Argos LC = 1,2,3
Filtered data do not include points on land
Filtered data only allow for 1 relocation every 4 horus

Purpose of the script is to compute homerange (area) using 
least squares cross-validation including 50% and 95% contours.
An analysis of each turtle and an aggregate pre and post will be computed
h values are chosen based on best judgment and gst behavior  

```{r}
rm(list = ls())
#getwd()
#list.files()

#Section 1: Load libraries and set wd
library(readxl)
library(dplyr)
library(adehabitatHR)
library(readxl)
library(rgdal)
library(leaflet) 
library(ggplot2)

internet <- FALSE
save.figure <- F

# Minimum number of relocations per individual to be included in HR analysis
min_n <- 50

# a function to create a data frame with minimum number of data points per individual
# then convert geographic coordinates so HR can be computed. Creates a list of length
# four. tagproj is the projection definition, which is defined at the end of next chunk

make.HR.dataset <- function(data.all, ID.min_n, tagproj){
  selected <- dplyr::right_join(data.all, 
                                ID.min_n, 
                                by = "ArgosID")
  
  all.coords <- data.frame(x=selected$Lon1, 
                           y=selected$Lat1)
  
  coordinates(all.coords) <- ~ x + y
  proj4string(all.coords) <- CRS(latlong)
  all.utm <- spTransform(all.coords, tagproj)

  byID.coords <- data.frame(x=selected$Lon1, 
                            y=selected$Lat1,
                            ID = as.factor(selected$ArgosID))
  coordinates(byID.coords) <- ~ x + y
  proj4string(byID.coords) <- CRS(latlong)
  byID.utm <- spTransform(byID.coords, tagproj)
  return(list(all.coords = all.coords,
              all.utm = all.utm,
              byID.coords = byID.coords,
              byID.utm = byID.utm))
}

HR.bvnorm.fcn <- function(all.utm, 
                          byID.utm, 
                          h, 
                          hlim=c(0.03, 1.5), 
                          grid=300, extent = 1){
  
  all.kd <- kernelUD(all.utm, 
                     h = h,  
                     hlim = hlim, 
                     grid = grid,
                     extent = extent,
                     kern = "bivnorm")
  
  Area.all <- kernel.area(all.kd, 
                          percent = c(50, 95),
                          unin = c("m"),
                          unout = c("km2"), 
                          standardize = FALSE)

  byID.kd <- kernelUD(byID.utm, 
                      h = all.kd@h$h ,  
                      hlim = hlim, 
                      grid = grid,
                      extent = extent,
                      kern = "bivnorm")
  
  Area.byID <- kernel.area(byID.kd, 
                           percent = c(50, 95),
                           unin = c("m"),
                           unout = c("km2"), 
                           standardize = FALSE)

  bw <- all.kd@h$h ##bandwidth estimate
  #Area.50 <- Area.all["50"]
  #Area.95 <- Area.all["95"]
  
  #ver.50 <- getverticeshr(all.kd, 50)
  #ver.95 <- getverticeshr(all.kd, 95)
  
  return(list(bw = bw,
              all.kd = all.kd,
              byID.kd = byID.kd,
              area.all = Area.all,
              area.byID = Area.byID))
}

HR.analysis.step1 <- function(min_n, data.df, tagproj, grid=300){
  data.df %>% count(by = ArgosID) %>%
    filter(n > (min_n - 1)) %>%
    #dplyr::select(by) %>%
    rename(ArgosID = by) -> ID.min_n_day
  
  list.data <- make.HR.dataset(data.df, ID.min_n_day, tagproj)

  kd.href <- kernelUD(list.data$all.utm, 
                      h="href",  
                      grid=grid,
                      kern = "bivnorm")
  
  kd.LSCV <- kernelUD(list.data$all.utm, 
                      h="LSCV",  
                      hlim = c(0.03, 1.5), 
                      grid=300,
                      kern = "bivnorm")
  return(list(kd.href = kd.href,
              kd.LSCV = kd.LSCV,
              IDs = ID.min_n_day,
              list.data = list.data))
}

HR.analysis <- function(h.multiplier, kd.href, data.list, grid = 300){
  h.adhoc <- h.multiplier * kd.href@h$h

  kd.adhoc <- vector(mode = "list", length = length(h.adhoc))
  for (k in 1:length(h.adhoc)){
    kd.adhoc[[k]] <- kernelUD(data.list$all.utm, 
                              h = h.adhoc[k],  
                              grid = grid,
                              kern = "bivnorm")
    
  }

  # make dataframes of vertices:
  ver.95.adhoc <- lapply(kd.adhoc, 
                         FUN = getverticeshr, 
                         percent = 95)

  ver.95.adhoc.tmp <- lapply(ver.95.adhoc, 
                             FUN = spTransform, 
                             CRS = CRS("+proj=longlat"))

  ver.95.adhoc.list <- lapply(ver.95.adhoc.tmp,
                              FUN = broom::tidy)

  for (k in 1:length(ver.95.adhoc.list)){
    ver.95.adhoc.list[[k]] <- ver.95.adhoc.list[[k]] %>% 
      mutate(h = h.adhoc[k]) %>%
      mutate(h.fac = as.factor(round(h, digits = 2))) %>%
      mutate(h.multip = h.multiplier[k])
  }

  # rbind all:
  ver.95.adhoc.df <- do.call("rbind", ver.95.adhoc.list)

  p.h.adhoc <- ggplot(data = ver.95.adhoc.df,
                      aes(x = long, y = lat,
                          group = group)) + 
    geom_polygon() + 
    coord_map() + facet_grid(. ~ h.multip) +
    facet_wrap( ~ h.multip, nrow = 3) + 
    labs(x = "", y = "")+ 
    theme(axis.text.x = element_text(angle = 90)) +
    scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                       limits = c(-117.15, -117.09))+
    scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                       limits = c(32.60, 32.66))

  return(list(figure = p.h.adhoc,
              ver.95 = ver.95.adhoc.df,
              h = h.adhoc))
}

compute.area <- function(h, list.data, grid=300){
  HR <- HR.bvnorm.fcn(list.data$all.utm, 
                      list.data$byID.utm, 
                      h = h, 
                      hlim=c(0.03, 1.5), 
                      grid=grid, extent = 1)
  bw <- HR$all.kd@h$h ##bandwidth estimate

  return(list(area.50 = HR$area.all["50"],
              area.95 = HR$area.all["95"],
              ver.50 = getverticeshr(HR$all.kd, 50),
              ver.95 = getverticeshr(HR$all.kd, 95)))
}

```

Get some base layer maps here:

```{r}
# just use the 2014 eelgrass data - there are old data files also
SDBay.eelg.2014 <- spTransform(readOGR(dsn = "GISfiles/Features",
                                       layer = "SD_Baywide_Eelgrass_2014_Final",
                                       verbose = F),
                               CRS("+proj=longlat +datum=WGS84"))
SDBay.eelg.2014.df <- broom::tidy(SDBay.eelg.2014)

SDBay.eelg.2008 <- spTransform(readOGR(dsn = "GISfiles/Features",
                                       layer = "SD_Baywide_Eelgrass_2008",
                                       verbose = F),
                               CRS("+proj=longlat +datum=WGS84"))
SDBay.eelg.2008.df <- broom::tidy(SDBay.eelg.2008)

if (internet){
  sdbay.all <- ggmap::get_map(location = c(lon = -117.15,
                                           lat = 32.65),
                       zoom = 12,
                       maptype = "satellite",
                       color = "bw",
                       filename = 'sdbay_all',
                       force = F)
  saveRDS(sdbay.all, file = 'RData/sdbay_all.rds')

  sdbay.south <- ggmap::get_map(location = c(lon = -117.117,
                                             lat = 32.625),
                         zoom = 14,
                         maptype = "satellite",
                         color = "bw",
                         filename = 'sdbay_south',
                         force = F)
  saveRDS(sdbay.south, file = 'RData/sdbay_south.rds')

  sdbay.med <- ggmap::get_map(location = c(lon =  -117.117,
                                           lat = 32.625),
                       zoom = 13,
                       maptype = "satellite",
                       color = "bw",
                       filename = 'sdbay_med',
                       force = F)
  saveRDS(sdbay.med, file = 'RData/sdbay_med.rds')
} else {
  sdbay.all <- readRDS(file = 'RData/sdbay_all.rds')
  sdbay.south <- readRDS(file = 'RData/sdbay_south.rds')
  sdbay.med <- readRDS(file = 'RData/sdbay_med.rds')
}

map.sdbay.zm <- ggmap::ggmap(sdbay.all)

map.sdbay.south <- ggmap::ggmap(sdbay.south)

map.sdbay.med <- ggmap::ggmap(sdbay.med)

# read in the SDB shape file:
SDB.shape <- readOGR(dsn = "GISFiles", layer = "sd_bay")
SDBay <- spTransform(readOGR(dsn = "GISfiles",
                             layer = "sd_bay",
                             verbose = F),
                     CRS("+proj=longlat +datum=WGS84"))
SDBay.df <- broom::tidy(SDBay)

water <- spTransform(readOGR(dsn = "GISFiles", 
                             layer = "water",
                             verbose = F),
                     CRS("+proj=longlat +datum=WGS84"))
water.df <- broom::tidy(water) %>%
  filter(lat < 32.75 & lat > 32.58 & long > -117.25)

tagprj <- readOGR(dsn = "Tag_065_UTMzone11n", 
                  layer = "tag_065_project")
tagproj <- proj4string(tagprj)

# not sure what this part is doing... 
latlong = "+init=epsg:4326"
```

Section 2: read in data

Section 2.1: Pre

```{r}
ID.names <- function(name){
  x <- unlist(strsplit(name, '_'))[1]
  return(x)
}
dname <- "data/files_Apr2018_withNewTags/pre/"
pre.files <- dir(path = dname, 
                 pattern = "_inside_DayNight_4hrs_2018-07-11.csv")

pre.IDs <- unlist(lapply(pre.files, FUN = ID.names))

pre.all <- do.call(rbind, 
                   lapply(pre.files,
                          FUN = function(x) read.csv(paste0(dname, x)))) %>%
  mutate(ID.f = as.factor(ArgosID)) %>%
  filter(include == 1)


write.csv(pre.all, paste0(dname, "Pre_GPS_LC_all.csv"), 
          row.names=FALSE)

```

Plot the data points to see what they look like:

```{r}
map.pre <- map.sdbay.zm + 
  geom_polygon(data = SDBay.df,
               aes(x = long, y = lat)) +
               #fill = "blue",alpha = 0.6) + 
  geom_polygon(data = SDBay.eelg.2008.df,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = "green",
               alpha = 0.5) +
  geom_point(data = pre.all,
             aes(x = Lon1, y = Lat1, color = ID.f),
             alpha = 0.5)+ 
  # geom_polygon(data = water.df,
  #              aes(x = long,
  #                  y = lat,
  #                  group = group),
  #              fill = "blue",
  #              alpha = 0.2) +

  #coord_map() + 
  #labs(color = 'ARGOS ID') + 
  xlab('Longitude') + ylab('Latitude') + 
  theme(legend.title = element_text(size = 10, hjust = 0.5),
        legend.text = element_text(size = 8, vjust = 0),
        legend.position = "none")

plot(map.pre)

```



Do the same for post 

```{r}
dname <- "data/files_Apr2018_withNewTags/post/"
post.files <- dir(path = dname, 
                 pattern = "_inside_DayNight_4hrs_2018-07-11.csv")

post.IDs <- unlist(lapply(post.files, FUN = ID.names))

post.all <- do.call(rbind, 
                   lapply(post.files,
                          FUN = function(x) read.csv(paste0(dname, x)))) %>%
  mutate(ID.f = as.factor(ArgosID)) %>%
  filter(include == 1)

map.post <- map.sdbay.zm + 
   geom_polygon(data = SDBay.df,
               aes(x = long, y = lat)) +
               #fill = "blue",
               #alpha = 0.6) + 
  geom_polygon(data = SDBay.eelg.2014.df,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = "green",
               alpha = 0.6) +
  geom_point(data = post.all,
             aes(x = Lon1, y = Lat1, color = ID.f),
             alpha = 0.5)+ 
  labs(color = 'ARGOS ID') + 
  xlab('Longitude') + ylab('Latitude') + 
  theme(#legend.title = element_text(size = 10, hjust = 0.5),
        #legend.text = element_text(size = 8, vjust = 0),
        #legend.position = c(0.2, 0.5),
        legend.position = "none")

plot(map.post)
```

And probably we should inlude the new files into "post". Also, take out the one track that goes out the bay - north of 32.66N
```{r}
dname <- "data/files_Apr2018_withNewTags/new/"
new.files <- dir(path = dname, 
                 pattern = "_inside_DayNight_4hrs_2018-07-11.csv")

new.IDs <- unlist(lapply(new.files, FUN = ID.names))

new.all <- do.call(rbind, 
                   lapply(new.files,
                          FUN = function(x) read.csv(paste0(dname, x)))) %>%
   mutate(ID.f = as.factor(ArgosID)) %>%
 filter(include == 1)

post.all <- rbind(post.all, new.all) %>%
  filter(Lat1 < 32.66)

write.csv(post.all, paste0(dname, "Post_GPS_LC_all.csv"), 
          row.names=FALSE)

map.post <- map.sdbay.zm + 
  geom_polygon(data = SDBay.df,
               aes(x = long, y = lat)) + 
               #fill = "blue",
               #alpha = 0.6) + 
  geom_polygon(data = SDBay.eelg.2014.df,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = "green",
               alpha = 0.6) +geom_point(data = post.all,
             aes(x = Lon1, y = Lat1, color = ID.f),
             alpha = 0.5)+ 
  labs(color = 'ARGOS ID') + 
  xlab('Longitude') + ylab('Latitude') + 
  theme(#legend.title = element_text(size = 10, hjust = 0.5),
        #legend.text = element_text(size = 8, vjust = 0),
        #legend.position = c(0.2, 0.5),
    legend.position = "none")

plot(map.post)
```

We have a lot more individuals from the post period than the pre, so we need to do something about that... especially for computing HRs. 


Section 3: Compute HRs

```{r}
# when trying to compute HR for each individual, some don't have enough data
# extract those with at least 100 data points:

pre.kd <- HR.analysis.step1(min_n, pre.all, tagproj, grid = 300)
```

Do the same with post dataset - choose those with at least min_n data points. 

```{r}
post.kd <- HR.analysis.step1(min_n, post.all, tagproj, grid = 300)

```

Then the home range analysis starts here. First we need to figure out the smoothing parameter (bandwidth, h). There seem to be different methods and recommendations...

First, least-squares cross validation on the pre data:
```{r}
plotLSCV(pre.kd$kd.LSCV)

```

Referecne or optimum bandwidth is ~248 (see pre.kd.href), whereas the LSCV comes back with h = 25.9 (Pre.kd@h$h). According to Kie (2013), we should decrease href in increments of 0.10 and the best value is the smallest increment of href that 1. resulted in a contiguous rather than disjoint 95% kernel home-range polygon, and 2. contained no lacuna within the home range. 
```{r}
h.multiplier <-  seq(from = 0.1, to = 0.95, by = 0.05) 

h.adhoc.pre <- HR.analysis(h.multiplier, 
                           pre.kd$kd.href, 
                           pre.kd$list.data, 
                           grid = 300)
  
plot(h.adhoc.pre$figure)


```

Looking at these plots, multiplier = 0.6 may be the smallest value with a contiguous 95% UD.  This is equivalent of h = 148.96 ~ 145.  

```{r}
## Section 3.1.2
##Visually optimized hlim = c(0.565,1.5), grid=300
# grid values from 50 to 300 don't change the outcome;
# extent values from 1 to 200 don't change the outcome either

h.pre <- 145

pre.HR <- compute.area(h.pre, pre.kd$list.data, grid = 300)
writeOGR(obj = pre.HR$ver.50, 
         dsn = "shapefiles_July2018/pre_HR_50.shp",
         layer="Pre.50", 
         driver="ESRI Shapefile", 
         overwrite_layer=TRUE)

writeOGR(obj = pre.HR$ver.95, 
         dsn = "shapefiles_July2018/pre_HR_95.shp",
         layer="Pre.95", 
         driver="ESRI Shapefile", 
         overwrite_layer=TRUE)
# plot(pre.ver.50, axes = TRUE)
# plot(pre.ver.95, axes = TRUE)
#points(pre.all.utm, col="blue")

```


Do the same for the post data - here we need to look at subsampling individuals. First, use all data.

First, least-squares cross validation on the pre data:
```{r}
plotLSCV(post.kd$kd.LSCV)

```

```{r}

h.adhoc.post <- HR.analysis(h.multiplier, 
                            post.kd$kd.href, 
                            post.kd$list.data, 
                            grid = 300)
  
plot(h.adhoc.post$figure)

```

For post data, multiplier = 0.4 may be the smallest value with a contiguous 95% UD.  This is equivalent of h = 97.16. So, h = 100 may be okay?


```{r}
## Section 3.1.2
##Visually optimized hlim = c(0.565,1.5), grid=300
h.post <- 100
post.HR <- compute.area(h.post, post.kd$list.data, grid = 300)
writeOGR(obj = post.HR$ver.50, 
         dsn = "shapefiles_July2018/post_HR_50.shp",
         layer="Post.50", 
         driver="ESRI Shapefile", 
         overwrite_layer=TRUE)

writeOGR(obj = post.HR$ver.95, 
         dsn = "shapefiles_July2018/post_HR_95.shp",
         layer="Post.95", 
         driver="ESRI Shapefile", 
         overwrite_layer=TRUE)

# plot(post.ver.50, axes = TRUE)
# plot(post.ver.95, axes = TRUE)
#points(pre.all.utm, col="blue")
```

Select all possible combinations of 6 (ID.pre.min_n) individuals from the post data. There are 8008 possible combinations when min_n = 50. It takes a bit of time, I select 1000 of them. Because of the sample size decreases, I use h.pre for this.

```{r echo=FALSE, results="hide"}
run.date <- "2018-07-17"
if (!file.exists(paste0("RData/areas_combos_", run.date, ".rds"))){
  combos <- combn(1:dim(ID.post.min_n)[1], 
                  dim(ID.pre.min_n)[1])
  combos <- combos[, sample(1:ncol(combos), 
                            size = 1000)]
  IDs <- ver.95.df.list <- pts.df.list <- vector(mode = "list", length = ncol(combos))
  area.95 <- area.50 <- vector(mode = "numeric", length = ncol(combos))
  
  #p.list <- list()
  for (k in 1:ncol(combos)){
    
    ID.post.tmp <- ID.post.min_n[combos[,k], ]
    tmp.list <- make.HR.dataset(post.all, ID.post.tmp, tagproj)
    
    tmp.HR <- HR.bvnorm.fcn(all.utm = tmp.list$all.utm,
                            byID.utm = tmp.list$byID.utm,
                            h = h.pre,
                            hlim=c(0.03, 1.5),
                            grid=300, extent = 1)
    
    ver.95.df.list <- broom::tidy(spTransform(getverticeshr(tmp.HR$all.kd, 95),
                                              CRS("+proj=longlat")))
    
    pts.df.list <- data.frame(lon = tmp.list$all.coords@coords[,1],
                              lat = tmp.list$all.coords@coords[,2])
    
    # p.list[[k]] <- ggplot() +
    #   geom_polygon(data = tmp.df, aes(x = long, y = lat, group = group)) +
    #   geom_point(data = pts.df, aes(x = lon, y = lat),
    #              color = "green") + coord_map()
    
    area.50[k] <- tmp.HR$area.all["50"]
    area.95[k] <- tmp.HR$area.all["95"]
    
    IDs[[k]] <- ID.post.tmp[,1]
  }
  
  areas.combos <- list(area95 = area.95,
                       area50 = area.50,
                       ID = IDs,
                       polygon = ver.95.df.list,
                       points = pts.df.list)
  
  saveRDS(areas.combos,
          file = paste0("RData/areas_combos_", Sys.Date(), ".rds"))
  
} else {
  areas.combos <- readRDS(file = paste0("RData/areas_combos_", 
                                        run.date, ".rds"))
}

```

Compare the randomized areas and the pre area.
```{r}
dif.50.df <- data.frame(dif = areas.combos$area50 - pre.HR$area.50)
dif.95.df <- data.frame(dif = areas.combos$area95 - pre.HR$area.95)

hist.dif.50 <- ggplot(data = dif.50.df) + 
  geom_histogram(aes(x = dif), binwidth = 0.1) +
  labs(x = "Difference in area", y = "Count")

#plot(hist.dif.50)

hist.dif.95 <- ggplot(data = dif.95.df) + 
  geom_histogram(aes(x = dif), binwidth = 0.15) +
  labs(x = "Difference in area", y = "Count")

#plot(hist.dif.95)

quantile(dif.50.df$dif, c(0.025, 0.05, 0.10, 0.15, 0.50, 0.975))
quantile(dif.95.df$dif, c(0.025, 0.05, 0.10, 0.15, 0.50, 0.975))

dif.50.df %>% count(dif>0)

dif.95.df %>% count(dif > 0)


```


The 95 percentiles of UDs ranged from 5.95 km2 to 7.89 when using six turtles at a time. The computed 95% UD for the pre dataset was 6.31, which was about 10 percentile of UDs for the post dataset. This indicated the UDs increased from the pre to post periods. 

Compare between night and day and pre and post:
```{r}
# pre day vs pre night:
pre.all %>% filter(day1night2 == 1) -> pre.day

pre.kd.day <- HR.analysis.step1(min_n, pre.day, tagproj, grid = 300)

plotLSCV(pre.kd.day$kd.LSCV)
```

```{r}
h.adhoc.pre.day <- HR.analysis(h.multiplier, 
                               pre.kd.day$kd.href, 
                               pre.kd.day$list.data, 
                               grid = 300)
plot(h.adhoc.pre.day$figure)

```

multiplier = 0.7 may be good. 

```{r}
h.pre.day <- pre.kd.day$kd.href@h$h * 0.7
# or use the same value as before

pre.HR.day <- compute.area(h.pre.day, pre.kd.day$list.data, grid = 300)
writeOGR(obj = pre.HR.day$ver.50, 
         dsn = "shapefiles_July2018/pre_HR_day_50.shp",
         layer="Pre.day.50", 
         driver="ESRI Shapefile", 
         overwrite_layer=TRUE)

writeOGR(obj = pre.HR.day$ver.95, 
         dsn = "shapefiles_July2018/pre_HR_day_95.shp",
         layer="Pre.day.95", 
         driver="ESRI Shapefile", 
         overwrite_layer=TRUE)
```

For night:
```{r}
pre.all %>% filter(day1night2 == 2) -> pre.night
pre.kd.night <- HR.analysis.step1(min_n, pre.night, tagproj, grid = 300)
plotLSCV(pre.kd.night$kd.LSCV)

```

```{r}
h.adhoc.pre.night <- HR.analysis(h.multiplier, 
                                 pre.kd.night$kd.href, 
                                 pre.kd.night$list.data, 
                                 grid = 300)
plot(h.adhoc.pre.night$figure)

```

multiplier = 0.5 may be good. 

```{r}
h.pre.night <- pre.kd.night$kd.href@h$h * 0.5
# or use the same value as before

pre.HR.night <- compute.area(h.pre.night, pre.kd.night$list.data, grid = 300)
writeOGR(obj = pre.HR.night$ver.50, 
         dsn = "shapefiles_July2018/pre_HR_night_50.shp",
         layer="Pre.night.50", 
         driver="ESRI Shapefile", 
         overwrite_layer=TRUE)

writeOGR(obj = pre.HR.night$ver.95, 
         dsn = "shapefiles_July2018/pre_HR_night_95.shp",
         layer="Pre.night.95", 
         driver="ESRI Shapefile", 
         overwrite_layer=TRUE)
```

Do the same with the post period
```{r}
# pre day vs pre night:
post.all %>% filter(day1night2 == 1) -> post.day

post.kd.day <- HR.analysis.step1(min_n, post.day, tagproj, grid = 300)

plotLSCV(post.kd.day$kd.LSCV)
```

```{r}
h.adhoc.post.day <- HR.analysis(h.multiplier, 
                               post.kd.day$kd.href, 
                               post.kd.day$list.data, 
                               grid = 300)
plot(h.adhoc.post.day$figure)

```

multiplier = 0.4 may be good. 

```{r}
h.post.day <- round(post.kd.day$kd.href@h$h * 0.4)
# or use the same value as before

post.HR.day <- compute.area(h.post.day, post.kd.day$list.data, grid = 300)
writeOGR(obj = post.HR.day$ver.50, 
         dsn = "shapefiles_July2018/post_HR_day_50.shp",
         layer="Post.day.50", 
         driver="ESRI Shapefile", 
         overwrite_layer=TRUE)

writeOGR(obj = post.HR.day$ver.95, 
         dsn = "shapefiles_July2018/post_HR_day_95.shp",
         layer="Post.day.95", 
         driver="ESRI Shapefile", 
         overwrite_layer=TRUE)

```

For night:
```{r}
post.all %>% filter(day1night2 == 2) -> post.night
post.kd.night <- HR.analysis.step1(min_n, post.night, tagproj, grid = 300)
plotLSCV(post.kd.night$kd.LSCV)

```

```{r}
h.adhoc.post.night <- HR.analysis(h.multiplier, 
                                 post.kd.night$kd.href, 
                                 post.kd.night$list.data, 
                                 grid = 300)
plot(h.adhoc.post.night$figure)

```

multiplier = 0.45 may be good. 

```{r}
h.post.night <- round(post.kd.night$kd.href@h$h * 0.45)
# or use the same value as before

post.HR.night <- compute.area(h.post.night, post.kd.night$list.data, grid = 300)

writeOGR(obj = post.HR.night$ver.50, 
         dsn = "shapefiles_July2018/post_HR_night_50.shp",
         layer="Post.night.50", 
         driver="ESRI Shapefile", 
         overwrite_layer=TRUE)

writeOGR(obj = post.HR.night$ver.95, 
         dsn = "shapefiles_July2018/post_HR_night_95.shp",
         layer="Post.night.95", 
         driver="ESRI Shapefile", 
         overwrite_layer=TRUE)

```


Make a plot for pre using all data:
```{r}

pre.ver.50.df <- broom::tidy(spTransform(pre.HR$ver.50, CRS("+proj=longlat")))
pre.ver.95.df <- broom::tidy(spTransform(pre.HR$ver.95, CRS("+proj=longlat")))

map.pre.HR <- map.sdbay.zm + 
  geom_polygon(data = SDBay.df,
               aes(x = long, y = lat)) +
               #fill = "blue",alpha = 0.6) + 
  geom_polygon(data = SDBay.eelg.2008.df,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = "green",
               alpha = 0.5) +
  geom_polygon(data = pre.ver.95.df,
               aes(x = long, y = lat,
                   group = group),
               fill = "cornsilk",
               alpha = 0.6) + 
  geom_polygon(data = pre.ver.50.df,
               aes(x = long, y = lat,
                   group = group),
               fill = "red3",
               alpha = 0.6) + 
  # geom_point(data = pre.all,
  #            aes(x = Lon1, y = Lat1),
  #            alpha = 0.5,
  #            size = 0.2)+ 
  # geom_polygon(data = water.df,
  #              aes(x = long,
  #                  y = lat,
  #                  group = group),
  #              fill = "blue",
  #              alpha = 0.2) +

  #coord_map() + 
  #labs(color = 'ARGOS ID') + 
  xlab('Longitude') + ylab('Latitude') + 
  theme(#legend.title = element_text(size = 10, hjust = 0.5),
        #legend.text = element_text(size = 8, vjust = 0),
        legend.position = "none")


#plot(map.pre.HR)
```

Make a plot for pre day:
```{r}

pre.day.ver.50.df <- broom::tidy(spTransform(pre.HR.day$ver.50, CRS("+proj=longlat")))
pre.day.ver.95.df <- broom::tidy(spTransform(pre.HR.day$ver.95, CRS("+proj=longlat")))

map.pre.day.HR <- map.sdbay.zm + 
  geom_polygon(data = SDBay.df,
               aes(x = long, y = lat)) +
               #fill = "blue",alpha = 0.6) + 
  geom_polygon(data = SDBay.eelg.2008.df,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = "green",
               alpha = 0.5) +
  geom_polygon(data = pre.day.ver.95.df,
               aes(x = long, y = lat,
                   group = group),
               fill = "cornsilk",
               alpha = 0.6) + 
  geom_polygon(data = pre.day.ver.50.df,
               aes(x = long, y = lat,
                   group = group),
               fill = "red3",
               alpha = 0.6) + 
  # geom_point(data = pre.all,
  #            aes(x = Lon1, y = Lat1),
  #            alpha = 0.5,
  #            size = 0.2)+ 
  # geom_polygon(data = water.df,
  #              aes(x = long,
  #                  y = lat,
  #                  group = group),
  #              fill = "blue",
  #              alpha = 0.2) +

  #coord_map() + 
  #labs(color = 'ARGOS ID') + 
  xlab('Longitude') + ylab('Latitude') + 
  theme(#legend.title = element_text(size = 10, hjust = 0.5),
        #legend.text = element_text(size = 8, vjust = 0),
        legend.position = "none")


#plot(map.pre.day.HR)
```

Make a plot for pre night:
```{r}

pre.night.ver.50.df <- broom::tidy(spTransform(pre.HR.night$ver.50, CRS("+proj=longlat")))
pre.night.ver.95.df <- broom::tidy(spTransform(pre.HR.night$ver.95, CRS("+proj=longlat")))

map.pre.night.HR <- map.sdbay.zm + 
  geom_polygon(data = SDBay.df,
               aes(x = long, y = lat)) +
               #fill = "blue",alpha = 0.6) + 
  geom_polygon(data = SDBay.eelg.2008.df,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = "green",
               alpha = 0.5) +
  geom_polygon(data = pre.night.ver.95.df,
               aes(x = long, y = lat,
                   group = group),
               fill = "cornsilk",
               alpha = 0.6) + 
  geom_polygon(data = pre.night.ver.50.df,
               aes(x = long, y = lat,
                   group = group),
               fill = "red3",
               alpha = 0.6) + 
  # geom_point(data = pre.all,
  #            aes(x = Lon1, y = Lat1),
  #            alpha = 0.5,
  #            size = 0.2)+ 
  # geom_polygon(data = water.df,
  #              aes(x = long,
  #                  y = lat,
  #                  group = group),
  #              fill = "blue",
  #              alpha = 0.2) +

  #coord_map() + 
  #labs(color = 'ARGOS ID') + 
  xlab('Longitude') + ylab('Latitude') + 
  theme(#legend.title = element_text(size = 10, hjust = 0.5),
        #legend.text = element_text(size = 8, vjust = 0),
        legend.position = "none")


#plot(map.pre.night.HR)
```

Make a plot for post using all data:
```{r}

post.ver.50.df <- broom::tidy(spTransform(post.HR$ver.50, CRS("+proj=longlat")))
post.ver.95.df <- broom::tidy(spTransform(post.HR$ver.95, CRS("+proj=longlat")))

map.post.HR <- map.sdbay.zm + 
  geom_polygon(data = SDBay.df,
               aes(x = long, y = lat)) +
               #fill = "blue",alpha = 0.6) + 
  geom_polygon(data = SDBay.eelg.2014.df,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = "green",
               alpha = 0.5) +
  geom_polygon(data = post.ver.95.df,
               aes(x = long, y = lat,
                   group = group),
               fill = "cornsilk",
               alpha = 0.6) + 
  geom_polygon(data = post.ver.50.df,
               aes(x = long, y = lat, 
                   group = group),
               fill = "red3",
               alpha = 0.6) + 
  # geom_point(data = post.all,
  #            aes(x = Lon1, y = Lat1),
  #            alpha = 0.5,
  #            size = 0.2)+ 
  # # geom_polygon(data = water.df,
  #              aes(x = long,
  #                  y = lat,
  #                  group = group),
  #              fill = "blue",
  #              alpha = 0.2) +

  #coord_map() + 
  #labs(color = 'ARGOS ID') + 
  xlab('Longitude') + ylab('Latitude') + 
  theme(#legend.title = element_text(size = 10, hjust = 0.5),
        #legend.text = element_text(size = 8, vjust = 0),
        legend.position = "none")
#plot(map.post.HR)
```

Make a plot for post day:
```{r}

post.day.ver.50.df <- broom::tidy(spTransform(post.HR.day$ver.50, CRS("+proj=longlat")))
post.day.ver.95.df <- broom::tidy(spTransform(post.HR.day$ver.95, CRS("+proj=longlat")))

map.post.day.HR <- map.sdbay.zm + 
  geom_polygon(data = SDBay.df,
               aes(x = long, y = lat)) +
               #fill = "blue",alpha = 0.6) + 
  geom_polygon(data = SDBay.eelg.2014.df,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = "green",
               alpha = 0.5) +
  geom_polygon(data = post.day.ver.95.df,
               aes(x = long, y = lat,
                   group = group),
               fill = "cornsilk",
               alpha = 0.6) + 
  geom_polygon(data = post.day.ver.50.df,
               aes(x = long, y = lat, 
                   group = group),
               fill = "red3",
               alpha = 0.6) + 
  # geom_point(data = post.all,
  #            aes(x = Lon1, y = Lat1),
  #            alpha = 0.5,
  #            size = 0.2)+ 
  # # geom_polygon(data = water.df,
  #              aes(x = long,
  #                  y = lat,
  #                  group = group),
  #              fill = "blue",
  #              alpha = 0.2) +

  #coord_map() + 
  #labs(color = 'ARGOS ID') + 
  xlab('Longitude') + ylab('Latitude') + 
  theme(#legend.title = element_text(size = 10, hjust = 0.5),
        #legend.text = element_text(size = 8, vjust = 0),
        legend.position = "none")

#plot(map.post.day.HR)
```


Make a plot for post night:
```{r}

post.night.ver.50.df <- broom::tidy(spTransform(post.HR.night$ver.50,
                                                CRS("+proj=longlat")))
post.night.ver.95.df <- broom::tidy(spTransform(post.HR.night$ver.95,
                                                CRS("+proj=longlat")))

map.post.night.HR <- map.sdbay.zm + 
  geom_polygon(data = SDBay.df,
               aes(x = long, y = lat)) +
               #fill = "blue",alpha = 0.6) + 
  geom_polygon(data = SDBay.eelg.2014.df,
               aes(x = long,
                   y = lat,
                   group = group),
               fill = "green",
               alpha = 0.5) +
  geom_polygon(data = post.night.ver.95.df,
               aes(x = long, y = lat,
                   group = group),
               fill = "cornsilk",
               alpha = 0.6) + 
  geom_polygon(data = post.night.ver.50.df,
               aes(x = long, y = lat, 
                   group = group),
               fill = "red3",
               alpha = 0.6) + 
  # geom_point(data = post.all,
  #            aes(x = Lon1, y = Lat1),
  #            alpha = 0.5,
  #            size = 0.2)+ 
  # # geom_polygon(data = water.df,
  #              aes(x = long,
  #                  y = lat,
  #                  group = group),
  #              fill = "blue",
  #              alpha = 0.2) +

  #coord_map() + 
  #labs(color = 'ARGOS ID') + 
  xlab('Longitude') + ylab('Latitude') + 
  theme(#legend.title = element_text(size = 10, hjust = 0.5),
        #legend.text = element_text(size = 8, vjust = 0),
        legend.position = "none")

#plot(map.post.night.HR)
```


```{r}
if (save.figure){
  ggsave(filename = paste0("figures/HR_pre_h_comp_", Sys.Date(), ".png"),
       plot = h.adhoc.pre$figure,
       dpi = 600,
       device = "png")
  ggsave(filename = paste0("figures/HR_post_h_comp_", Sys.Date(), ".png"),
         plot = h.adhoc.post$figure,
         dpi = 600,
         device = "png")
  ggsave(filename = paste0("figures/HR_pre_day_h_comp_", Sys.Date(), ".png"),
         plot = h.adhoc.pre.day$figure,
         dpi = 600,
         device = "png")
  ggsave(filename = paste0("figures/HR_pre_night_h_comp_", Sys.Date(), ".png"),
         plot = h.adhoc.pre.night$figure,
         dpi = 600,
         device = "png")
  ggsave(filename = paste0("figures/HR_post_day_h_comp_", Sys.Date(), ".png"),
         plot = h.adhoc.post.day$figure,
         dpi = 600,
         device = "png")
  ggsave(filename = paste0("figures/HR_post_night_h_comp_", Sys.Date(), ".png"),
         plot = h.adhoc.post.night$figure,
         dpi = 600,
         device = "png")
  ggsave(filename = paste0("figures/HR_pre_h", round(h.pre), "_", Sys.Date(), ".png"),
         plot = map.pre.HR,
         dpi = 600,
         device = "png")
  
  ggsave(filename = paste0("figures/HR_post_h", round(h.post), "_", Sys.Date(), ".png"),
         plot = map.post.HR,
         dpi = 600,
         device = "png")
  
  ggsave(filename = paste0("figures/HR_pre_day_h", 
                           round(h.pre.day), "_", Sys.Date(), ".png"),
         plot = map.pre.day.HR,
         dpi = 600,
         device = "png")
  
  ggsave(filename = paste0("figures/HR_post_day_h", 
                           round(h.post.day), "_", Sys.Date(), ".png"),
         plot = map.post.day.HR,
         dpi = 600,
         device = "png")
  
  ggsave(filename = paste0("figures/HR_pre_night_h", 
                           round(h.pre.night), "_", Sys.Date(), ".png"),
         plot = map.pre.night.HR,
         dpi = 600,
         device = "png")
  
  ggsave(filename = paste0("figures/HR_post_night_h", 
                           round(h.post.night), "_", Sys.Date(), ".png"),
         plot = map.post.night.HR,
         dpi = 600,
         device = "png")
  
  ggsave(filename = paste0("figures/HR95_difference_", 
                           Sys.Date(), ".png"),
         plot = hist.dif.95,
         dpi = 600,
         device = "png")

  ggsave(filename = paste0("figures/HR50_difference_", 
                           Sys.Date(), ".png"),
         plot = hist.dif.50,
         dpi = 600,
         device = "png")
}


#plot(map.post.HR)
```