---
title: "KDE vs. MCP"
output: html_notebook
---

Comparing the areas computed by KDE and MCP - trying to justify using MCP for showing the center of MCPs moved with changing temperature.

```{r}
rm(list = ls())
#getwd()
#list.files()

ifelse(Sys.info()[1] == 'Linux',
       source('~/Documents/R/tools/TomosFunctions.R'),
       source('~/R/tools/TomosFunctions.R'))

#Section 1: Load libraries and set wd
#library(readxl)
library(dplyr)
library(adehabitatHR)
library(rgdal)
library(leaflet) 
library(ggplot2)
library(lubridate)
library(tidyverse)

source("HR_analysis_fcns.R")

grid.value <- 1000
min_n <- 50
tagprj <- readOGR(dsn = "Tag_065_UTMzone11n", 
                  layer = "tag_065_project")

tagproj <- proj4string(tagprj)

# not sure what this part is doing... 
latlong = "+init=epsg:4326"

file.date <- "2018-10-31"
```

Read in the data files:

```{r}
pre.summary <-  read.csv(paste0("data/pre_sample_summary_", 
                                file.date, ".csv"))

pre.all <-  read.csv(paste0("data/Pre_GPS_LC_all_", 
                                   file.date, ".csv"))

post.summary <- read.csv(paste0("data/post_sample_summary_", 
                   file.date, ".csv"))

post.all <-  read.csv(paste0("data/Post_GPS_LC_all_",
                   file.date, ".csv"))

```

Then do the KDE first on the pre data:

```{r, cache=T}
# when trying to compute HR for each individual, some don't have enough data
# extract those with at least 50 data points:

pre.kd <- HR.analysis.step1(min_n, pre.all, 
                            tagproj, 
                            grid = grid.value)

UD.95.pre.eachID <- UD.75.pre.eachID <- UD.50.pre.eachID <- vector(mode = "list", 
                                               length = length(pre.kd$list.data$eachID.utm))
h.pre.eachID <- h.multip.pre.eachID <- vector(mode = "numeric", length = length(pre.kd$list.data$eachID.utm))

for (k in 1:length(pre.kd$list.data$eachID.utm)){
  
  dat.utm <- pre.kd$list.data$eachID.utm[[k]]
  best.h <- find.h.adhoc(dat.utm)
  h.pre.eachID[k] <- round(best.h$h)
  h.multip.pre.eachID[k] <- best.h$h.multip
  UD <- kernelUD(dat.utm, 
                 h = h.pre.eachID[k], 
                 kern = "bivnorm", 
                 grid = grid.value)
  UD.95.pre.eachID[[k]] <- getverticeshr(UD, 95)
  UD.75.pre.eachID[[k]] <- getverticeshr(UD, 75)
  UD.50.pre.eachID[[k]] <- getverticeshr(UD, 50)
}

tmp.pre.95 <- lapply(UD.95.pre.eachID, 
                     FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))

tmp.pre.75 <- lapply(UD.75.pre.eachID, 
                     FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))

tmp.pre.50 <- lapply(UD.50.pre.eachID, 
                     FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))


for (k in 1:length(tmp.pre.95)){
  tmp.pre.50[[k]] <- mutate(tmp.pre.50[[k]], 
                            ID = pre.kd$list.data$unique.ID[k])
  tmp.pre.95[[k]] <- mutate(tmp.pre.95[[k]], 
                            ID = pre.kd$list.data$unique.ID[k])
  tmp.pre.75[[k]] <- mutate(tmp.pre.75[[k]], 
                            ID = pre.kd$list.data$unique.ID[k])}

pre.eachID.ver.95.df <- do.call("rbind", tmp.pre.95)
pre.eachID.ver.75.df <- do.call("rbind", tmp.pre.75)
pre.eachID.ver.50.df <- do.call("rbind", tmp.pre.50)


```

Then compute MCP using all data:
```{r}
pre.all %>% count(by = ArgosID) %>%
    filter(n > (min_n - 1)) %>%
    #dplyr::select(by) %>%
    rename(ArgosID = by) -> pre.ID.min_n_day

pre.list <- make.HR.dataset(pre.all, pre.ID.min_n_day, tagproj)

pre.ID <- pre.list$unique.ID

pre.mcp1.50 <- pre.mcp1.75 <- pre.mcp1.95 <- vector(mode = "list", length = length(pre.ID))
for (i in 1:length(pre.ID)){
  pre.turtle1 <- pre.list$eachID.utm[[i]]  
  pre.turtle1.time <- pre.list$eachID.time[[i]]
  pre.turtle1.time$dif.time <- difftime(pre.turtle1.time$UTC,
                                         pre.turtle1.time$UTC[1], 
                                         units = "days")
  pre.turtle1.latlon <- pre.list$eachID.coords[[i]]
  pre.mcp1.50[[i]] <- mcp(pre.turtle1, 
                          percent = 50, 
                          unin = "m", unout = "km2")
  pre.mcp1.75[[i]] <- mcp(pre.turtle1, 
                          percent = 75, 
                          unin = "m", unout = "km2")
  pre.mcp1.95[[i]] <- mcp(pre.turtle1, 
                          percent = 95, 
                          unin = "m", unout = "km2")
  
}

tmp.pre.95 <- lapply(pre.mcp1.95, 
                     FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))

tmp.pre.75 <- lapply(pre.mcp1.75, 
                     FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))

tmp.pre.50 <- lapply(pre.mcp1.50, 
                     FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))


for (k in 1:length(tmp.pre.95)){
  tmp.pre.50[[k]] <- mutate(tmp.pre.50[[k]], 
                            ID = pre.ID[k])
  tmp.pre.75[[k]] <- mutate(tmp.pre.75[[k]], 
                            ID = pre.ID[k])
  tmp.pre.95[[k]] <- mutate(tmp.pre.95[[k]], 
                            ID = pre.ID[k])
}

pre.MCP.95.df <- do.call("rbind", tmp.pre.95)
pre.MCP.75.df <- do.call("rbind", tmp.pre.75)
pre.MCP.50.df <- do.call("rbind", tmp.pre.50)

```



Do the same with post dataset - choose those with at least min_n data points. 

```{r, cache=T}
post.kd <- HR.analysis.step1(min_n, post.all, 
                             tagproj, 
                             grid = grid.value)

UD.95.post.eachID <- UD.75.post.eachID <- UD.50.post.eachID <- vector(mode = "list", 
                                               length = length(post.kd$list.data$eachID.utm))
h.post.eachID <- h.multip.post.eachID <- vector(mode = "numeric", length = length(post.kd$list.data$eachID.utm))

for (k in 1:length(post.kd$list.data$eachID.utm)){
  
  dat.utm <- post.kd$list.data$eachID.utm[[k]]
  best.h <- find.h.adhoc(dat.utm)
  h.post.eachID[k] <- round(best.h$h)
  h.multip.post.eachID[k] <- best.h$h.multip
  UD <- kernelUD(dat.utm, 
                 h = h.post.eachID[k], 
                 kern = "bivnorm", 
                 grid = grid.value)
  UD.95.post.eachID[[k]] <- getverticeshr(UD, 95)
  UD.75.post.eachID[[k]] <- getverticeshr(UD, 75)  
  UD.50.post.eachID[[k]] <- getverticeshr(UD, 50)
}

tmp.post.95 <- lapply(UD.95.post.eachID, 
                     FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))

tmp.post.75 <- lapply(UD.75.post.eachID, 
                     FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))
tmp.post.50 <- lapply(UD.50.post.eachID, 
                     FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))


for (k in 1:length(tmp.post.95)){
  tmp.post.50[[k]] <- mutate(tmp.post.50[[k]], 
                            ID = post.kd$list.data$unique.ID[k])
  tmp.post.75[[k]] <- mutate(tmp.post.75[[k]], 
                            ID = post.kd$list.data$unique.ID[k])
  tmp.post.95[[k]] <- mutate(tmp.post.95[[k]], 
                            ID = post.kd$list.data$unique.ID[k])
}

post.eachID.ver.95.df <- do.call("rbind", tmp.post.95)
post.eachID.ver.75.df <- do.call("rbind", tmp.post.75)
post.eachID.ver.50.df <- do.call("rbind", tmp.post.50)

```

Then for MCPs on post data.

```{r}
post.all %>% count(by = ArgosID) %>%
    filter(n > (min_n - 1)) %>%
    #dplyr::select(by) %>%
    rename(ArgosID = by) -> post.ID.min_n_day

post.list <- make.HR.dataset(post.all, post.ID.min_n_day, tagproj)

post.ID <- post.list$unique.ID

post.mcp1.50 <- post.mcp1.75 <- post.mcp1.95 <- vector(mode = "list", 
                                                       length = length(post.ID))
for (i in 1:length(post.ID)){
  post.turtle1 <- post.list$eachID.utm[[i]]  
  post.turtle1.time <- post.list$eachID.time[[i]]
  post.turtle1.time$dif.time <- difftime(post.turtle1.time$UTC,
                                         post.turtle1.time$UTC[1], 
                                         units = "days")
  post.turtle1.latlon <- post.list$eachID.coords[[i]]
  post.mcp1.50[[i]] <- mcp(post.turtle1, 
                           percent = 50, 
                           unin = "m", unout = "km2")
  post.mcp1.75[[i]] <- mcp(post.turtle1, 
                           percent = 75, 
                           unin = "m", unout = "km2")
  post.mcp1.95[[i]] <- mcp(post.turtle1, 
                           percent = 95, 
                           unin = "m", unout = "km2")
  
}

tmp.post.95 <- lapply(post.mcp1.95, 
                     FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))

tmp.post.75 <- lapply(post.mcp1.75, 
                     FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))
tmp.post.50 <- lapply(post.mcp1.50, 
                     FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))


for (k in 1:length(tmp.post.95)){
  tmp.post.50[[k]] <- mutate(tmp.post.50[[k]], 
                            ID = post.ID[k])
  tmp.post.75[[k]] <- mutate(tmp.post.75[[k]], 
                            ID = post.ID[k])
  tmp.post.95[[k]] <- mutate(tmp.post.95[[k]], 
                            ID = post.ID[k])
}

post.MCP.95.df <- do.call("rbind", tmp.post.95)
post.MCP.75.df <- do.call("rbind", tmp.post.75)
post.MCP.50.df <- do.call("rbind", tmp.post.50)

```

And save some stuff so I don't have to run this again unless necessary.

```{r}
KDE.out <- list(pre.50 = pre.eachID.ver.50.df,
                post.50 = post.eachID.ver.50.df,
                pre.75 = pre.eachID.ver.75.df,
                post.75 = post.eachID.ver.75.df,
                pre.95 = pre.eachID.ver.95.df,
                post.95 = post.eachID.ver.95.df)
MCP.out <- list(pre.50 = pre.MCP.50.df,
                post.50 = post.MCP.50.df,
                pre.75 = pre.MCP.75.df,
                post.75 = post.MCP.75.df,
                pre.95 = pre.MCP.95.df,
                post.95 = post.MCP.95.df)
data.list <- list(post = post.list, pre = pre.list)

out.list <- list(KDE = KDE.out, 
                 MCP = MCP.out, 
                 data = data.list)
saveRDS(out.list, file = "RData/KDEvsMCPout.rds")
```

