---
title: "KDE vs MCP plotting"
output: html_notebook
---

This file uses the output from KDEvsMCP.Rmd and creates plots to compare how the two methods differ in computing areas from the relocation data for SDB green turtles.

First setup libraries and some constants:
```{r, echo=FALSE}
rm(list = ls())
#getwd()
#list.files()

ifelse(Sys.info()[1] == 'Linux',
       source('~/Documents/R/tools/TomosFunctions.R'),
       source('~/R/tools/TomosFunctions.R'))

#Section 1: Load libraries and set wd
#library(readxl)
library(adehabitatHR)
library(rgdal)
library(leaflet) 
library(ggplot2)
library(lubridate)
library(dplyr)
library(tidyverse)

source("HR_analysis_fcns.R")

grid.value <- 1000
min_n <- 50
tagprj <- readOGR(dsn = "Tag_065_UTMzone11n", 
                  layer = "tag_065_project")

tagproj <- proj4string(tagprj)

# not sure what this part is doing... 
latlong = "+init=epsg:4326"

file.date <- "2018-10-31"
save.fig <- TRUE
```

```{r}
KDE.MCP.data <- readRDS("RData/KDEvsMCPout.rds")
KDE.out <- KDE.MCP.data$KDE
MCP.out <- KDE.MCP.data$MCP
post.data <- KDE.MCP.data$data$post
pre.data <- KDE.MCP.data$data$pre

post.data.df <- data.frame(cbind(post.data$byID.coords@data,
                                 post.data$byID.coords@coords)) %>%
  group_by(ID)
pre.data.df <- data.frame(cbind(pre.data$byID.coords@data,
                                 pre.data$byID.coords@coords))  %>%
  group_by(ID)
```

Then make plots. Pre period first.

First compare MCP 50% and 95%
```{r}
p.MCP.pre <- ggplot() + 
  geom_point(data = pre.data.df,
             aes(x = x, y = y)) +
  geom_polygon(data = MCP.out$pre.95,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightcyan",
               alpha = 0.8) +
  geom_polygon(data = MCP.out$pre.75,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "deepskyblue",
               alpha = 0.5) +
  
  geom_polygon(data = MCP.out$pre.50,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "blue4",
               alpha = 0.2) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65))
plot(p.MCP.pre)

if (save.fig)
  ggsave(plot = p.MCP.pre,
         filename = "figures/MCP_pre.png",
         device = "png",
         dpi = 600)
```

and KDE

```{r}
p.KDE.pre <- ggplot() + 
  geom_point(data = pre.data.df,
             aes(x = x, y = y)) +
  geom_polygon(data = KDE.out$pre.95,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 0.7) +
  geom_polygon(data = KDE.out$pre.75,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "indianred",
               alpha = 0.7) +
  
  geom_polygon(data = KDE.out$pre.50,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 0.4) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65))
plot(p.KDE.pre)

if (save.fig)
  ggsave(plot = p.KDE.pre,
         filename = "figures/KDE_pre.png",
         device = "png",
         dpi = 600)

```

```{r}
p.MCP.KDE.pre.50 <- ggplot() + 
  geom_point(data = pre.data.df,
             aes(x = x, y = y),
             color = "gray50") +
  geom_polygon(data = KDE.out$pre.50,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 0.6) +
  geom_polygon(data = MCP.out$pre.50,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "blue4",
               alpha = 0.6) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65))
plot(p.MCP.KDE.pre.50)

if (save.fig)
  ggsave(plot = p.MCP.KDE.pre.50,
         filename = "figures/MCP_KDE_50_pre.png",
         device = "png",
         dpi = 600)

```

75% for pre
```{r}
p.MCP.KDE.pre.75 <- ggplot() + 
    geom_point(data = pre.data.df,
             aes(x = x, y = y)) +
  geom_polygon(data = KDE.out$pre.75,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "indianred",
               alpha = 0.7) +
  geom_polygon(data = MCP.out$pre.75,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "deepskyblue",
               alpha = 0.4) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65))
plot(p.MCP.KDE.pre.75)

if (save.fig)
  ggsave(plot = p.MCP.KDE.pre.75,
         filename = "figures/MCP_KDE_75_pre.png",
         device = "png",
         dpi = 600)

```


and 95% for pre

```{r}
p.MCP.KDE.pre.95 <- ggplot() + 
    geom_point(data = pre.data.df,
             aes(x = x, y = y)) +
  geom_polygon(data = KDE.out$pre.95,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 0.7) +
  geom_polygon(data = MCP.out$pre.95,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightcyan",
               alpha = 0.4) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65))
plot(p.MCP.KDE.pre.95)

if (save.fig)
  ggsave(plot = p.MCP.KDE.pre.95,
         filename = "figures/MCP_KDE_95_pre.png",
         device = "png",
         dpi = 600)

```

And for the post period
```{r}
p.MCP.post <- ggplot() + 
  geom_point(data = post.data.df,
             aes(x = x, y = y),
             color = "gray50") +
  geom_polygon(data = MCP.out$post.95,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightcyan",
               alpha = 0.7) +
  geom_polygon(data = MCP.out$post.75,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "deepskyblue",
               alpha = 0.7) +
  geom_polygon(data = MCP.out$post.50,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "blue4",
               alpha = 0.6) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 3) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.08)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65))
plot(p.MCP.post)

if (save.fig)
  ggsave(plot = p.MCP.post,
         filename = "figures/MCP_post.png",
         device = "png",
         dpi = 600)

```

and KDE

```{r}
p.KDE.post <- ggplot() + 
  geom_point(data = post.data.df,
             aes(x = x, y = y)) +
  geom_polygon(data = KDE.out$post.95,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 0.7) +
  geom_polygon(data = KDE.out$post.75,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "indianred",
               alpha = 0.7) +
  
  geom_polygon(data = KDE.out$post.50,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 0.6) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 3) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.08)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65))
plot(p.KDE.post)

if (save.fig)
  ggsave(plot = p.KDE.post,
         filename = "figures/KDE_post.png",
         device = "png",
         dpi = 600)

```

```{r}
p.MCP.KDE.post.50 <- ggplot() + 
  geom_point(data = post.data.df,
             aes(x = x, y = y),
             color = "gray60") +
  geom_polygon(data = KDE.out$post.50,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 0.7) +
  geom_polygon(data = MCP.out$post.50,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "blue4",
               alpha = 0.7) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 3) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65))
plot(p.MCP.KDE.post.50)

if (save.fig)
  ggsave(plot = p.MCP.KDE.post.50,
         filename = "figures/MCP_KDE_50_post.png",
         device = "png",
         dpi = 600)

```

75%
```{r}
p.MCP.KDE.75.post <- ggplot() + 
  geom_point(data = post.data.df,
             aes(x = x, y = y),
             color = "gray50") +
  geom_polygon(data = KDE.out$post.75,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "indianred",
               alpha = 0.6) +
  geom_polygon(data = MCP.out$post.75,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "deepskyblue",
               alpha = 0.4) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 3) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.08)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65))
plot(p.MCP.KDE.75.post)

if (save.fig)
  ggsave(plot = p.MCP.KDE.75.post,
         filename = "figures/MCP_KDE_75_post.png",
         device = "png",
         dpi = 600)

```


And post 95%

```{r}
p.MCP.KDE.95.post <- ggplot() + 
  geom_point(data = post.data.df,
             aes(x = x, y = y),
             color = "gray50") +
  geom_polygon(data = KDE.out$post.95,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 0.6) +
  geom_polygon(data = MCP.out$post.95,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightcyan",
               alpha = 0.4) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 3) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.08)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65))
plot(p.MCP.KDE.95.post)

if (save.fig)
  ggsave(plot = p.MCP.KDE.95.post,
         filename = "figures/MCP_KDE_95_post.png",
         device = "png",
         dpi = 600)

```

So, they seem to be comparable for these home range estimations. If anything, MCP underestimates the range. For the purpose of finding the centers of polygons, MCPs should be fine. Especially 95% MCP seems to capture what my eyes see. 