---
title: "MCP per day"
output: html_notebook
---

Computes a minimum convex polygon for each individual per day - is there a pattern in seaons or possibly temperature?


```{r}
rm(list = ls())
#getwd()
#list.files()

ifelse(Sys.info()[1] == 'Linux',
       source('~/Documents/R/tools/TomosFunctions.R'),
       source('~/R/tools/TomosFunctions.R'))

#Section 1: Load libraries and set wd
#library(readxl)
library(dplyr)
library(adehabitatHR)
library(rgdal)
library(leaflet) 
library(ggplot2)
library(lubridate)
library(tidyverse)
library(readr)

source("HR_analysis_fcns.R")

tagprj <- readOGR(dsn = "Tag_065_UTMzone11n", 
                  layer = "tag_065_project")
tagproj <- proj4string(tagprj)
latlong = "+init=epsg:4326"

min_n <- 50
n_days <- 7   # # days pooled to create a MCP
MCP.percent <- 95

save.fig <- TRUE
save.files <- TRUE
```

Read in post and pre datasets

```{r, include=FALSE, echo=FALSE, message=FALSE}
col.defs <- cols(ID = col_integer(),
                 ArgosID = col_integer(),
                 Message_Type = col_character(),
                 TransmissionDateTime = col_datetime(format = "%Y-%m-%d %H:%M:%S"),
                 LC = col_integer(),
                 Residual = col_double(),
                 Lat1 = col_double(),
                 Lon1 = col_double(),
                 inside = col_integer(),
                 UTCDateTime = col_datetime(format = "%Y-%m-%d %H:%M:%S"),
                 LocalDateTime = col_datetime(format = "%Y-%m-%d %H:%M:%S"),
                 Date2 = col_datetime(format = "%Y-%m-%d"),
                 LocalSunrise = col_datetime(format = "%Y-%m-%d %H:%M:%S"),
                 LocalSunset = col_datetime(format = "%Y-%m-%d %H:%M:%S"),
                 day1night2 = col_integer(),
                 row = col_integer(),
                 include = col_integer(),
                 hr = col_integer(),
                 ID.f = col_integer(),
                 DaysSinceFirst = col_double())

post.all <- read_csv("data/Post_GPS_LC_all_2018-09-18.csv",
                     col_types = col.defs)

post.all %>% count(by = ArgosID) %>%
    dplyr::filter(n > (min_n - 1)) %>%
    #dplyr::select(by) %>%
    rename(ArgosID = by) -> post.ID.min_n_day

post.list <- make.HR.dataset(post.all, post.ID.min_n_day, tagproj)

post.ID <- post.list$unique.ID

mcp.post <- mcp.post.area <- post.dates <- vector(mode = "list", 
                                               length = length(post.ID))
post.area.df <- data.frame(date = as.POSIXct(character()), 
                           area = numeric(), ID = numeric(),
                           lat.center = numeric(),
                           lon.center = numeric(),
                           days = numeric())
i <- r <- 1
for (i in 1:length(post.ID)){
  post.turtle1 <- post.list$eachID.utm[[i]]  
  post.turtle1.time <- post.list$eachID.time[[i]]
  post.turtle1.time$dif.time <- difftime(post.turtle1.time$UTC,
                                         post.turtle1.time$UTC[1], 
                                         units = "days")
  post.turtle1.latlon <- post.list$eachID.coords[[i]]

  n.steps <- as.numeric(floor(floor(max(post.turtle1.time$dif.time))/n_days))
  mcp1.area <- mcp1 <- dates <- center <- vector(mode = "list", 
                                                 length = n.steps)
  min.day <- 0
  n <- 1
  for (n in 1:n.steps){
    post.turtle1.ndays <- post.turtle1[post.turtle1.time$dif.time >= min.day &
                                         post.turtle1.time$dif.time < (min.day + n_days),]
    post.turtle1.time.ndays <- post.turtle1.time[post.turtle1.time$dif.time >= min.day &
                                                   post.turtle1.time$dif.time < (min.day + n_days),]
    post.turtle1.ndays.latlon <- post.turtle1.latlon[post.turtle1.time$dif.time >= min.day &
                                                   post.turtle1.time$dif.time < (min.day + n_days),]
    if (nrow(post.turtle1.ndays@coords) > 4){
      mcp1.area[[n]] <- mcp.area(post.turtle1.ndays, 
                                 percent = MCP.percent, 
                                 unin = "m", unout = "km2",
                                 plotit = FALSE)
      
      mcp1[[n]] <- mcp(post.turtle1.ndays,
                       percent = MCP.percent,
                       unin = "m", unout = "km2")
      
      dates[[n]] <- min(post.turtle1.time.ndays$UTC)
      center[[n]] <- rgeos::gCentroid(post.turtle1.ndays.latlon)
      post.area.df[r, "area"] <- mcp1.area[[n]]
      post.area.df[r, "date"] <- dates[[n]]
      post.area.df[r, "lat.center"] <- center[[n]]$y
      post.area.df[r, "lon.center"] <- center[[n]]$x
      post.area.df[r, "days"] <- as.numeric( post.turtle1.time.ndays[ nrow( post.turtle1.time.ndays), 
                                                                     "dif.time"]) 
    }
    post.area.df[r, "ID"] <- post.ID[i]
    min.day <- min.day + n_days
    r <- r + 1
  }
  #mcp.all[[i]] <- mcp1
  mcp.post.area[[i]] <- compact(mcp1.area)
  post.dates[[i]] <- compact(dates)
  
  tmp.post <- lapply(compact(mcp1), 
                     FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))
  
  # Do not use date to index... maybe just use n of n.steps... 
  # need to add ID also

  for (k in 1:length(tmp.post)){
    tmp.post[[k]] <- mutate(tmp.post[[k]], 
                            k = k,
                            ID = post.ID[i])  
  }

  mcp.post[[i]] <- do.call("rbind", tmp.post)

}

# combine areas and dates into a dataframe
post.area.df %>% na.omit() %>%
  mutate(month = month(date),
         doy = yday(date)) -> post.area.df



```

```{r}
p.7 <- ggplot() + 
  geom_point(data = post.area.df,
             aes(x = doy, y = area, color = as.factor(ID)),
             size = 2) + 
  geom_path(data = post.area.df,
             aes(x = doy, y = area, color = as.factor(ID)))

print(p.7)
#pre.all <- read.csv("data/Pre_GPS_LC_all_2018-09-18.csv")
#pre.ID <- unique(pre.all$ArgosID)
if (save.fig)
  ggsave(plot = p.7,
         filename = paste0("figures/doyVsArea_", n_days, "days_post.png"),
         device = "png",
         dpi = 600)
```

Do the same with the pre period
```{r, include=FALSE, message=FALSE, echo=FALSE}
pre.all <- read_csv("data/Pre_GPS_LC_all_2018-09-18.csv",
                     col_types = col.defs)

pre.all %>% count(by = ArgosID) %>%
    filter(n > (min_n - 1)) %>%
    #dplyr::select(by) %>%
    rename(ArgosID = by) -> pre.ID.min_n_day

pre.list <- make.HR.dataset(pre.all, pre.ID.min_n_day, tagproj)

pre.ID <- pre.list$unique.ID

mcp.pre <- mcp.pre.area <- pre.dates <- vector(mode = "list", 
                                               length = length(pre.ID))
pre.area.df <- data.frame(date = as.POSIXct(character()), 
                          area = numeric(), 
                          ID = numeric(),
                          lat.center = numeric(),
                          lon.center = numeric(),
                          days = numeric())
r <- 1
for (i in 1:length(pre.ID)){
  pre.turtle1 <- pre.list$eachID.utm[[i]]  
  pre.turtle1.time <- pre.list$eachID.time[[i]]
  pre.turtle1.time$dif.time <- difftime(pre.turtle1.time$UTC,
                                         pre.turtle1.time$UTC[1], 
                                         units = "days")
  pre.turtle1.latlon <- pre.list$eachID.coords[[i]]
  n.steps <- as.numeric(floor(floor(max(pre.turtle1.time$dif.time))/n_days))
  mcp1.area <- mcp1 <- dates <- center <- vector(mode = "list", length = n.steps)
  min.day <- 0
  for (n in 1:n.steps){
    pre.turtle1.ndays <- pre.turtle1[pre.turtle1.time$dif.time >= min.day &
                                         pre.turtle1.time$dif.time < (min.day + n_days),]
    pre.turtle1.time.ndays <- pre.turtle1.time[pre.turtle1.time$dif.time >= min.day &
                                                   pre.turtle1.time$dif.time < (min.day + n_days),]
  
    pre.turtle1.ndays.latlon <- pre.turtle1.latlon[pre.turtle1.time$dif.time >= min.day &
                                                   pre.turtle1.time$dif.time < (min.day + n_days),]
    
    if (nrow(pre.turtle1.ndays@coords) > 4){
      mcp1.area[[n]] <- mcp.area(pre.turtle1.ndays, 
                                 percent = MCP.percent, 
                                 unin = "m", unout = "km2",
                                 plotit = FALSE)
      
      mcp1[[n]] <- mcp(pre.turtle1.ndays,
                       percent = MCP.percent,
                       unin = "m", unout = "km2")

      dates[[n]] <- min(pre.turtle1.time.ndays$UTC)
      center[[n]] <- rgeos::gCentroid(pre.turtle1.ndays.latlon)
      pre.area.df[r, "area"] <- mcp1.area[[n]]
      pre.area.df[r, "date"] <- dates[[n]]
      pre.area.df[r, "lat.center"] <- center[[n]]$y
      pre.area.df[r, "lon.center"] <- center[[n]]$x
      pre.area.df[r, "days"] <- as.numeric( pre.turtle1.time.ndays[ nrow( pre.turtle1.time.ndays), 
                                                                     "dif.time"])
    }
    min.day <- min.day + n_days
    pre.area.df[r, "ID"] <- pre.ID[i]
    r <- r + 1
  }
  
  mcp.pre.area[[i]] <- compact(mcp1.area)
  pre.dates[[i]] <- compact(dates)
  
  tmp.pre <- lapply(compact(mcp1), 
                    FUN = function(x) broom::tidy(spTransform(x, CRS("+proj=longlat"))))
  
  for (k in 1:length(tmp.pre)){
    tmp.pre[[k]] <- mutate(tmp.pre[[k]], 
                            k = k,
                            ID = post.ID[i])  
  }

  mcp.pre[[i]] <- do.call("rbind", tmp.pre)
}

# combine areas and dates into a dataframe
pre.area.df %>% na.omit() %>%
  mutate(month = month(date),
         doy = yday(date)) -> pre.area.df

```


```{r}
p.8 <- ggplot() + 
  geom_point(data = pre.area.df,
             aes(x = doy, y = area, color = as.factor(ID)),
             size = 2) +
  geom_line(data = pre.area.df,
             aes(x = doy, y = area, color = as.factor(ID)))

if (save.fig)
  ggsave(plot = p.8,
         filename = paste0("figures/doyVsArea_", n_days, "days_pre.png"),
         device = "png",
         dpi = 600)

```

```{r}
print(p.8)
```



Is there any relationship with water temp?

```{r, echo=FALSE, message=FALSE, include=FALSE}
pre.area.df$PP <- 0
post.area.df$PP <- 1
area.df <- rbind(pre.area.df, post.area.df)
wtemp <- min_wtemp <- max_wtemp <- SD_wtemp <- vector(mode = "numeric", 
                                                      length = nrow(area.df))

# lagged by 14 days
wtemp_14 <- min_wtemp_14 <- max_wtemp_14 <- SD_wtemp_14 <- vector(mode = "numeric", 
                                                      length = nrow(area.df))

# lagged by 7 days
wtemp_7 <- min_wtemp_7 <- max_wtemp_7 <- SD_wtemp_7 <- vector(mode = "numeric", 
                                                      length = nrow(area.df))

k <- 1

for (k in 1:nrow(area.df)){
    begin.date <- date(area.df[k, "date"])
    end.date <- date(area.df[k, "date"] + days(n_days - 1))
    tmp.1 <- tmp.summary(begin.date, end.date)
    tmp.14 <- tmp.summary(begin.date-days(14), begin.date)
    tmp.7 <- tmp.summary(begin.date - days(7), begin.date)

    wtemp[k] <- tmp.1$mean
    min_wtemp[k] <- tmp.1$min
    max_wtemp[k] <- tmp.1$max
    SD_wtemp[k] <- tmp.1$SD
    wtemp_7[k] <- tmp.7$mean
    min_wtemp_7[k] <- tmp.7$min
    max_wtemp_7[k] <- tmp.7$max
    SD_wtemp_7[k] <- tmp.7$SD
    wtemp_14[k] <- tmp.14$mean
    min_wtemp_14[k] <- tmp.14$min
    max_wtemp_14[k] <- tmp.14$max
    SD_wtemp_14[k] <- tmp.14$SD

    
}

area.df$wtemp <- unlist(wtemp)
area.df$min_wtemp <- unlist(min_wtemp)
area.df$max_wtemp <- unlist(max_wtemp)
area.df$SD_wtemp <- unlist(SD_wtemp)
area.df$dif_wtemp <- area.df$max_wtemp - area.df$min_wtemp

area.df$wtemp_7 <- unlist(wtemp_7)
area.df$min_wtemp_7 <- unlist(min_wtemp_7)
area.df$max_wtemp_7 <- unlist(max_wtemp_7)
area.df$SD_wtemp_7 <- unlist(SD_wtemp_7)
area.df$dif_wtemp_7 <- area.df$max_wtemp_7 - area.df$min_wtemp_7

area.df$wtemp_14 <- unlist(wtemp_14)
area.df$min_wtemp_14 <- unlist(min_wtemp_14)
area.df$max_wtemp_14 <- unlist(max_wtemp_14)
area.df$SD_wtemp_14 <- unlist(SD_wtemp_14)
area.df$dif_wtemp_14 <- area.df$max_wtemp_14 - area.df$min_wtemp_14

```


```{r}
p.1 <- ggplot(data = area.df) +
  geom_point(aes(x = wtemp, y = area, 
                 color = as.factor(PP)),
             size = 3) #+ 
  #facet_grid(. ~ ID) + 
  #facet_wrap( ~ ID, nrow = 4)

#print(p.1)
if (save.fig)
  ggsave(plot = p.1,
         filename = paste0("figures/wtempVsArea_", n_days, "days.png"),
         device = "png",
         dpi = 600)

```

```{r}
print(p.1)
```


```{r}
p.1_7 <- ggplot(data = area.df) +
  geom_point(aes(x = wtemp_7, y = area, 
                 color = as.factor(PP)),
             size = 3) #+ 
  #facet_grid(. ~ ID) + 
  #facet_wrap( ~ ID, nrow = 4)

#print(p.1)
if (save.fig)
  ggsave(plot = p.1_7,
         filename = paste0("figures/wtemp_7VsArea_", n_days, "days.png"),
         device = "png",
         dpi = 600)

```

```{r}
print(p.1_7)
```

```{r}
p.1_14 <- ggplot(data = area.df) +
  geom_point(aes(x = wtemp_14, y = area, 
                 color = as.factor(PP)),
             size = 3) +
  labs(title = "14 day lag")
  #facet_grid(. ~ ID) + 
  #facet_wrap( ~ ID, nrow = 4)

#print(p.1)
if (save.fig)
  ggsave(plot = p.1_14,
         filename = paste0("figures/wtemp_14VsArea_", n_days, "days.png"),
         device = "png",
         dpi = 600)

```

```{r}
print(p.1_14)
```

Any pattern with respect to day of year?
```{r}
area.df %>% mutate(doy = yday(date)) -> area.df
area.df %>% group_by(ID) %>% 
  summarise(lat.first = first(lat.center),
            lon.first = first(lon.center),
            PP = first(PP),
            date.first = first(date),
            area.first = first(area),
            days.first = first(days),
            wtemp.first = first(wtemp),
            min.wtemp.first = first(min_wtemp),
            max.wtemp.first = first(max_wtemp),
            SD.wtemp.first = first(SD_wtemp),
            wtemp_7.first = first(wtemp_7),
            min.wtemp_7.first = first(min_wtemp_7),
            max.wtemp_7.first = first(max_wtemp_7),
            SD.wtemp_7.first = first(SD_wtemp_7),
            wtemp_14.first = first(wtemp_14),
            min.wtemp_14.first = first(min_wtemp_14),
            max.wtemp_14.first = first(max_wtemp_14),
            SD.wtemp_14.first = first(SD_wtemp_14)) -> area.first.df

if (save.files)
  write.csv(area.df, 
            file = paste0("data/MCP_area_df_", n_days, "days.csv"),
            quote = FALSE,
            row.names = FALSE)

p.2 <- ggplot(data = area.df) + 
  geom_point(aes(x = doy, y = area, color = wtemp,
                 shape = as.factor(PP)),
             size = 3,
             alpha = 0.5)
print(p.2)

if (save.fig)
  ggsave(plot = p.2,
         filename = paste0("figures/doyVsAreaVsWtemp_", n_days, "days.png"),
         device = "png",
         dpi = 600)

```

Latitude?

```{r}
p.3 <- ggplot(data = filter(area.df, PP == 0)) + 
  geom_point(aes(x = wtemp, 
                 y = lat.center, 
                 color = as.factor(ID),
                 size = doy)) + 
  geom_path(aes(x = wtemp, 
                 y = lat.center, 
                 color = as.factor(ID))) + 
  # geom_point(data = filter(area.first.df, PP == 0),
  #            aes(x = wtemp.first,
  #                y = lat.first,
  #                color = as.factor(ID)),
  #            size = 4) + 
  labs(y = "Center of MCP (latitude)",
       y = "Mean water temperature (C)") + 

  theme(legend.position = "none")
print(p.3)

if (save.fig)
  ggsave(plot = p.3,
         filename = paste0("figures/wtempVsLatCenter_", n_days, "days_pre.png"),
         device = "png",
         dpi = 600)

```
There is an increasing relationship between water temperature and the centers of MCPs for the pre period. 


```{r}
p.3_7 <- ggplot(data = filter(area.df, PP == 0)) + 
  geom_point(aes(x = wtemp_7, 
                 y = lat.center, 
                 color = as.factor(ID),
                 size = doy)) + 
  geom_path(aes(x = wtemp_7, 
                 y = lat.center, 
                 color = as.factor(ID))) + 
  # geom_point(data = filter(area.first.df, PP == 0),
  #            aes(x = wtemp_7.first,
  #                y = lat.first,
  #                color = as.factor(ID)),
  #            size = 4)
  labs(y = "Center of MCP (latitude)",
       x = "Mean water temperature over 7 days (C)") + 

  theme(legend.position = "none")
print(p.3_7)

if (save.fig)
  ggsave(plot = p.3_7,
         filename = paste0("figures/wtemp_7VsLatCenter_", n_days, "days_pre.png"),
         device = "png",
         dpi = 600)

```

```{r}
p.3_14 <- ggplot(data = filter(area.df, PP == 0)) + 
  geom_point(aes(x = wtemp_14, 
                 y = lat.center, 
                 color = as.factor(ID),
                 size = doy)) + 
  geom_path(aes(x = wtemp_14, 
                 y = lat.center, 
                 color = as.factor(ID))) + 
  # geom_point(data = filter(area.first.df, PP == 0),
  #            aes(x = wtemp_14.first,
  #                y = lat.first,
  #                color = as.factor(ID)),
  #            size = 4)
  labs(y = "Center of MCP (latitude)",
       x = "Mean water temperature over 14 days (C)") + 

  theme(legend.position = "none")

print(p.3_14)

if (save.fig)
  ggsave(plot = p.3_14,
         filename = paste0("figures/wtemp_14VsLatCenter_", n_days, "days_pre.png"),
         device = "png",
         dpi = 600)

```

Longitude

```{r}
p.13 <- ggplot(data = filter(area.df, PP == 0)) + 
  geom_point(aes(y = wtemp, 
                 x = lon.center, 
                 color = as.factor(ID),
                 size = doy)) + 
  geom_path(aes(y = wtemp, 
                 x = lon.center, 
                 color = as.factor(ID))) + 
  # geom_point(data = filter(area.first.df, PP == 0),
  #            aes(y = wtemp.first,
  #                x = lon.first,
  #                color = as.factor(ID)),
  #            size = 4)
  labs(x = "Center of MCP (longitude)",
       y = "Mean water temperature (C)") + 

  theme(legend.position = "none")
print(p.13)

if (save.fig)
  ggsave(plot = p.13,
         filename = paste0("figures/wtempVsLonCenter_", n_days, "days_pre.png"),
         device = "png",
         dpi = 600)

```

And the decreasing one with longitude. 

```{r}
p.13_7 <- ggplot(data = filter(area.df, PP == 0)) + 
  geom_point(aes(y = wtemp_7, 
                 x = lon.center, 
                 color = as.factor(ID),
                 size = doy)) + 
  geom_path(aes(y = wtemp_7, 
                 x = lon.center, 
                 color = as.factor(ID))) + 
  # geom_point(data = filter(area.first.df, PP == 0),
  #            aes(y = wtemp_7.first,
  #                x = lon.first,
  #                color = as.factor(ID)),
  #            size = 4)
  labs(x = "Center of MCP (longitude)",
       y = "Mean water temperature over 7 days (C)") + 

  theme(legend.position = "none")

print(p.13_7)

if (save.fig)
  ggsave(plot = p.13_7,
         filename = paste0("figures/wtemp_7VsLonCenter_", n_days, "days_pre.png"),
         device = "png",
         dpi = 600)

```


```{r}
p.13_14 <- ggplot(data = filter(area.df, PP == 0)) + 
  geom_point(aes(y = wtemp_14, 
                 x = lon.center, 
                 color = as.factor(ID),
                 size = doy)) + 
  geom_path(aes(y = wtemp_14, 
                 x = lon.center, 
                 color = as.factor(ID))) + 
  # geom_point(data = filter(area.first.df, PP == 0),
  #            aes(y = wtemp_14.first,
  #                x = lon.first,
  #                color = as.factor(ID)),
  #            size = 4)
  labs(x = "Center of MCP (longitude)",
       y = "Mean water temperature over 14 days (C)") + 

  theme(legend.position = "none")
print(p.13_14)

if (save.fig)
  ggsave(plot = p.13_14,
         filename = paste0("figures/wtemp_14VsLonCenter_", n_days, "days_pre.png"),
         device = "png",
         dpi = 600)

```

```{r}
p.4 <- ggplot(data = filter(area.df, PP == 1)) + 
  geom_point(aes(x = wtemp, 
                 y = lat.center, 
                 color = as.factor(ID),
                 size = doy))+
  geom_path(aes(x = wtemp, 
                 y = lat.center, 
                 color = as.factor(ID))) + 
  # geom_point(data = filter(area.first.df, PP == 1),
  #            aes(x = wtemp.first,
  #                y = lat.first,
  #                color = as.factor(ID)),
  #            size = 4)
    labs(y = "Center of MCP (latitude)",
       x = "Mean water temperature (C)") + 

  theme(legend.position = "none")

print(p.4)

if (save.fig)
  ggsave(plot = p.4,
         filename = paste0("figures/wtempVsLatCenter_", 
                           n_days, "days_post.png"),
         device = "png",
         dpi = 600)
```

The water temp vs latitude center relationship is a bit whacky... For the post period, there also is an increasing relationship but a few turtles in the lower end makes it difficult to generalize. 


```{r}
p.4_7 <- ggplot(data = filter(area.df, PP == 1)) + 
  geom_point(aes(x = wtemp_7, 
                 y = lat.center, 
                 color = as.factor(ID),
                 size = doy))+
  geom_path(aes(x = wtemp_7, 
                 y = lat.center, 
                 color = as.factor(ID))) + 
  # geom_point(data = filter(area.first.df, PP == 1),
  #            aes(x = wtemp_7.first,
  #                y = lat.first,
  #                color = as.factor(ID)),
  #            size = 4)
  labs(y = "Center of MCP (latitude)",
       x = "Mean water temperature over 7 days (C)") + 

  theme(legend.position = "none")

print(p.4_7)

if (save.fig)
  ggsave(plot = p.4_7,
         filename = paste0("figures/wtemp_7VsLatCenter_", 
                           n_days, "days_post.png"),
         device = "png",
         dpi = 600)
```


```{r}
p.4_14 <- ggplot(data = filter(area.df, PP == 1)) + 
  geom_point(aes(x = wtemp_14, 
                 y = lat.center, 
                 color = as.factor(ID),
                 size = doy))+
  geom_path(aes(x = wtemp_14, 
                 y = lat.center, 
                 color = as.factor(ID))) + 
  # geom_point(data = filter(area.first.df, PP == 1),
  #            aes(x = wtemp_14.first,
  #                y = lat.first,
  #                color = as.factor(ID)),
  #            size = 4)
  labs(y = "Center of MCP (latitude)",
       x = "Mean water temperature over 14 days (C)") + 

  theme(legend.position = "none")

print(p.4_14)

if (save.fig)
  ggsave(plot = p.4_14,
         filename = paste0("figures/wtemp_14VsLatCenter_", 
                           n_days, "days_post.png"),
         device = "png",
         dpi = 600)
```


```{r}
p.12 <- ggplot(data = filter(area.df, PP == 1)) + 
  geom_point(aes(y = wtemp, 
                 x = lon.center, 
                 color = as.factor(ID),
                 size = doy))+
  geom_path(aes(y = wtemp, 
                 x = lon.center, 
                 color = as.factor(ID))) + 
  # geom_point(data = filter(area.first.df, PP == 1),
  #            aes(y = wtemp.first,
  #                x = lon.first,
  #                color = as.factor(ID)),
  #            size = 4)
    labs(x = "Center of MCP (longitude)",
       y = "Mean water temperature (C)") + 

  theme(legend.position = "none")

print(p.12)

if (save.fig)
  ggsave(plot = p.12,
         filename = paste0("figures/wtempVsLonCenter_", 
                           n_days, "days_post.png"),
         device = "png",
         dpi = 600)
```

Longitude doesn't seem to show the strong relationship found in the pre period. 


```{r}
p.12_7 <- ggplot(data = filter(area.df, PP == 1)) + 
  geom_point(aes(y = wtemp_7, 
                 x = lon.center, 
                 color = as.factor(ID),
                 size = doy))+
  geom_path(aes(y = wtemp_7, 
                 x = lon.center, 
                 color = as.factor(ID))) + 
  # geom_point(data = filter(area.first.df, PP == 1),
  #            aes(y = wtemp_7.first,
  #                x = lon.first,
  #                color = as.factor(ID)),
  #            size = 4)
  labs(x = "Center of MCP (longitude)",
       y = "Mean water temperature over 7 days (C)") + 
  
  theme(legend.position = "none")

print(p.12_7)

if (save.fig)
  ggsave(plot = p.12_7,
         filename = paste0("figures/wtemp_7VsLonCenter_", 
                           n_days, "days_post.png"),
         device = "png",
         dpi = 600)
```


```{r}
p.12_14 <- ggplot(data = filter(area.df, PP == 1)) + 
  geom_point(aes(y = wtemp_14, 
                 x = lon.center, 
                 color = as.factor(ID),
                 size = doy))+
  geom_path(aes(y = wtemp_14, 
                 x = lon.center, 
                 color = as.factor(ID))) + 
  # geom_point(data = filter(area.first.df, PP == 1),
  #            aes(y = wtemp_14.first,
  #                x = lon.first,
  #                color = as.factor(ID)),
  #            size = 4)
  labs(x = "Center of MCP (longitude)",
       y = "Mean water temperature over 14 days (C)") + 
  theme(legend.position = "none")

print(p.12_14)

if (save.fig)
  ggsave(plot = p.12_14,
         filename = paste0("figures/wtemp_14VsLonCenter_", 
                           n_days, "days_post.png"),
         device = "png",
         dpi = 600)
```


Did the center of MCPs changed with sampling time? 
```{r}
p.5 <- ggplot(data = dplyr::filter(area.df, PP == 0)) +
  geom_point(aes(x = days, 
                 y = lat.center, 
                 color = as.factor(ID),
                 size = doy)) + 
  geom_path(aes(x = days, 
                y = lat.center, 
                color = as.factor(ID))) + 
  theme(legend.position = "none")

print(p.5)
if (save.fig)
  ggsave(plot = p.5,
         filename = paste0("figures/daysVsLatCenter_", n_days, "days_pre.png"),
         device = "png",
         dpi = 600)
```


```{r}
p.6 <- ggplot(data = dplyr::filter(area.df, PP == 1)) +
  geom_point(aes(x = days, 
                 y = lat.center, 
                 color = as.factor(ID),
                 size = doy)) + 
  geom_path(aes(x = days, 
                y = lat.center, 
                color = as.factor(ID))) +
  theme(legend.position = "none")

print(p.6)
if (save.fig)
  ggsave(plot = p.6,
         filename = paste0("figures/daysVsLatCenter_", n_days, "days_post.png"),
         device = "png",
         dpi = 600)
```

```{r}
p.11 <- ggplot(data = dplyr::filter(area.df, PP == 1)) +
  geom_point(aes(y = days, 
                 x = lon.center, 
                 color = as.factor(ID),
                 size = doy)) + 
  geom_path(aes(y = days, 
                x = lon.center, 
                color = as.factor(ID))) + 
  theme(legend.position = "none")

print(p.11)
if (save.fig)
  ggsave(plot = p.11,
         filename = paste0("figures/daysVsLonCenter_", n_days, "days_post.png"),
         device = "png",
         dpi = 600)
```

Try days vs area:
```{r}
p.9 <- ggplot(data = dplyr::filter(area.df, PP == 0)) +
  geom_point(aes(x = days, 
                 y = area, 
                 color = as.factor(ID)),
             size = 2) + 
    geom_line(aes(x = days, 
                 y = area, 
                 color = as.factor(ID))) + 
  theme(legend.position = "none")

print(p.9)
if (save.fig)
  ggsave(plot = p.9,
         filename = paste0("figures/daysVsArea_", n_days, "days_pre.png"),
         device = "png",
         dpi = 600)
```

And for the post period:
```{r}
p.10 <- ggplot(data = dplyr::filter(area.df, PP == 1)) +
  geom_point(aes(x = days, 
                 y = area, 
                 color = as.factor(ID),
                 size = doy)) + 
    geom_line(aes(x = days, 
                 y = area, 
                 color = as.factor(ID))) + 
  theme(legend.position = "none")

print(p.10)
if (save.fig)
  ggsave(plot = p.10,
         filename = paste0("figures/daysVsArea_", n_days, "days_post.png"),
         device = "png",
         dpi = 600)
```


Visual inspection of how the MCPs moved for each individual
```{r}
mcp.post.df <- do.call("rbind", mcp.post)
#id.1 <- filter(mcp.post.df, ID == 126065)
p.MCP.post <- ggplot(data = mcp.post.df) + 
  geom_polygon(aes(x = long, y = lat,
                   fill = as.factor(k)),
               color = "black",
               alpha = 0.4) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 3) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.13, -117.11),
                     limits = c(-117.133, -117.09)) +
  scale_y_continuous(breaks = c(32.61, 32.63),
                     limits = c(32.60, 32.65)) + 
  theme(legend.position = "none")

plot(p.MCP.post)
if (save.fig)
  ggsave(plot = p.MCP.post,
         filename = paste0("figures/MCPvsTimeByID_", n_days, "days_post.png"),
         device = "png",
         dpi = 600)
```

There is no particular pattern, except may be 152315 moving a bit north? 

```{r}
mcp.pre.df <- do.call("rbind", mcp.pre)
p.MCP.pre <- ggplot(data = mcp.pre.df) + 
  geom_polygon(aes(x = long, y = lat,
                   fill = as.factor(k)),
               color = "black",
               alpha = 0.4) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.08)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65)) + 
  theme(legend.position = "none")

plot(p.MCP.pre)
if (save.fig)
  ggsave(plot = p.MCP.pre,
         filename = paste0("figures/MCPvsTimeByID_", n_days, "days_pre.png"),
         device = "png",
         dpi = 600)
```


Visual analysis doesn't bring out any particular patterns... so let's try mixed-effects model with ID as a random effect.

```{r}
library(lme4)
area.df %>% dplyr::select(-"date") %>%
  scale() %>% as.data.frame() -> area.df.center.scale
#library(mgcv)
lat.fit.1 <- lmer(lat.center ~ PP + wtemp + wtemp_7 + wtemp_14 + SD_wtemp + (1 | ID), 
              data = area.df.center.scale)

lat.fit.2 <- lmer(lat.center ~ PP + wtemp + wtemp_7 + wtemp_14 + (1 | ID), 
              data = area.df.center.scale) 
lat.fit.3 <- lmer(lat.center ~ PP +  wtemp_7 + wtemp_14 + (1 | ID), 
              data = area.df.center.scale)
lat.fit.4 <- lmer(lat.center ~ wtemp_7 + wtemp_14 + (1 | ID), 
              data = area.df.center.scale) 
lat.fit.5 <- lmer(lat.center ~ wtemp_14 + (1 | ID), 
              data = area.df.center.scale)
lat.fit.6 <- lmer(lat.center ~ wtemp_7 + (1 | ID), 
              data = area.df.center.scale)
lat.fit.7 <- lmer(lat.center ~ wtemp + (1 | ID), 
              data = area.df.center.scale)
 
anova(lat.fit.1, lat.fit.2, lat.fit.3, lat.fit.4, 
      lat.fit.5, lat.fit.6, lat.fit.7)
summary(lat.fit.4)
lat.fit.list <- list(lat.fit.1, lat.fit.2, lat.fit.3, 
                     lat.fit.4, lat.fit.5, lat.fit.6, lat.fit.7)
 
#plot(fit.1)
```

```{r}
lon.fit.1 <- lmer(lon.center ~ PP + wtemp + wtemp_7 + wtemp_14 + SD_wtemp + (1 | ID), 
              data = area.df.center.scale)

lon.fit.2 <- lmer(lon.center ~ PP + wtemp + wtemp_7 + wtemp_14 + (1 | ID), 
              data = area.df.center.scale) 
lon.fit.3 <- lmer(lon.center ~ PP +  wtemp_7 + wtemp_14 + (1 | ID), 
              data = area.df.center.scale)
lon.fit.4 <- lmer(lon.center ~ wtemp_7 + wtemp_14 + (1 | ID), 
              data = area.df.center.scale) 
lon.fit.5 <- lmer(lon.center ~ wtemp_14 + (1 | ID), 
              data = area.df.center.scale)
lon.fit.6 <- lmer(lon.center ~ wtemp_7 + (1 | ID), 
              data = area.df.center.scale)
lon.fit.7 <- lmer(lon.center ~ wtemp + (1 | ID), 
              data = area.df.center.scale)
 
anova(lon.fit.1, lon.fit.2, lon.fit.3, lon.fit.4, 
      lon.fit.5, lon.fit.6, lon.fit.7)
summary(lon.fit.4)
lon.fit.list <- list(lon.fit.1, lon.fit.2, lon.fit.3, 
                     lon.fit.4, lon.fit.5, lon.fit.6, lon.fit.7)
 
fit.list <- list(lat = lat.fit.list,
                 lon = lon.fit.list)

if (save.files)
  saveRDS(fit.list, file = paste0("RData/fit_list_", n_days, "days.rds"))

```

