---
title: "Compare pre vs. post periods"
output: html_notebook
---

This file contains code to compare pre and post periods by randomly extracting the same number of individuals as the pre period from the post period without replacement and compare the calculated HR areas. It also looks at the northern most latitude of 95% and 50% UDs.

```{r}
rm(list = ls())

ifelse(Sys.info()[1] == 'Linux',
       source('~/Documents/R/tools/TomosFunctions.R'),
       source('~/R/tools/TomosFunctions.R'))

#library(readxl)
library(dplyr)
library(adehabitatHR)
library(rgdal)
library(leaflet) 
library(ggplot2)
library(lubridate)
library(tidyverse)
library(ggridges)

source("HR_analysis_fcns.R")

# internet <- F #TRUE
save.fig <- T

# Minimum number of relocations per individual to be included in HR analysis
min_n <- 50
#N.end <- 32.69   # approx Coronado bridge
N.end <- 32.66 # changed from 32.69 because 152314 had a gap in data points between ~32.65 and ~32.66 - seems like there was a different behavior south and north of 32.66

grid <- 1000
extent <- 1


source("HR_analysis_fcns.R")
tagprj <- readOGR(dsn = "Tag_065_UTMzone11n", 
                  layer = "tag_065_project")
tagproj <- proj4string(tagprj)

# this file was created in PreVsPostAnalysis_DayNight.Rmd
all.data.frames <- readRDS(file = "RData/PreVsPost_DayNight.RDS")
KD.eachID.pre.combined <- all.data.frames[[1]]
KD.eachID.post.combined<- all.data.frames[[2]] 
KD.eachID.pre.day <- all.data.frames[[3]]
KD.eachID.pre.night <- all.data.frames[[4]]
KD.eachID.post.day <- all.data.frames[[5]] 
KD.eachID.post.night <- all.data.frames[[6]] 
UD.post.95.latlon <- all.data.frames[[7]] 
UD.post.50.latlon <- all.data.frames[[8]] 
UD.pre.95.latlon <- all.data.frames[[9]] 
UD.pre.50.latlon <- all.data.frames[[10]] 
UD.pre.day.95.latlon <- all.data.frames[[11]] 
UD.pre.day.50.latlon <- all.data.frames[[12]]
UD.pre.night.95.latlon <- all.data.frames[[13]] 
UD.pre.night.50.latlon <- all.data.frames[[14]] 
UD.post.day.95.latlon <- all.data.frames[[15]]
UD.post.day.50.latlon <- all.data.frames[[16]] 
UD.post.night.95.latlon <- all.data.frames[[17]]
UD.post.night.50.latlon <- all.data.frames[[18]]
UD.pre.day.night.95.latlon <- all.data.frames[[19]]
UD.pre.day.night.50.latlon <- all.data.frames[[20]]
UD.post.day.night.95.latlon <- all.data.frames[[21]]
UD.post.day.night.50.latlon <- all.data.frames[[22]]

```

Load results from HR_analysis_GPS_LC_newtags_11July2018.Rmd. The following files contain raw data for pre period. First, look at each turtle for day and night combined. 

```{r, message=FALSE}

p.KDE.pre.combined <- ggplot() + 
  geom_polygon(data = KD.eachID.pre.combined$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 1.0) +

  geom_polygon(data = KD.eachID.pre.combined$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 1.0) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.14, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.595, 32.65))
plot(p.KDE.pre.combined)

if (save.fig)
  ggsave(plot = p.KDE.pre.combined,
         filename = "figures/KDE_pre_combined.png",
         device = "png",
         dpi = 600)
```


Next, post period data are loaded and UDs for day and night combined are computed.
```{r, message=FALSE}

p.KDE.post.combined <- ggplot() + 
  geom_polygon(data = KD.eachID.post.combined$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 1.0) +

  geom_polygon(data = KD.eachID.post.combined$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 1.0) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 3) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.14, -117.08)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.595, 32.66))
plot(p.KDE.post.combined)

if (save.fig)
  ggsave(plot = p.KDE.post.combined,
         filename = "figures/KDE_post_combined.png",
         device = "png",
         dpi = 600)
```


We then pull out just day time for the pre period. One turtle cannot be analyzed because there were not enough relocation points in the day time. 
```{r}

p.KDE.pre.day <- ggplot() + 
  geom_polygon(data = KD.eachID.pre.day$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 1.0) +

  geom_polygon(data = KD.eachID.pre.day$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 1.0) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.14, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.595, 32.645))
plot(p.KDE.pre.day)

if (save.fig)
  ggsave(plot = p.KDE.pre.day,
         filename = "figures/KDE_pre_day.png",
         device = "png",
         dpi = 600)

```

Pre-day KDEs for 44366 has two "dots"... what's going on there? 12/4/2018 - has been fixed. It was caused by "rounding" the estimated h value for this animal. Changed it to "ceiling" which eliminated the tiny "dots". 12/4/2018.

Do the same for the nighttime for the pre period and plot on top of the daytime UDs.

```{r}


p.KDE.pre.day.night <- ggplot() + 
  geom_polygon(data = KD.eachID.pre.day$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightcyan",
               alpha = 1.0) +
  
  geom_polygon(data = KD.eachID.pre.day$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "blue4",
               alpha = 1.0) +

  geom_polygon(data = KD.eachID.pre.night$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 0.3) +

  geom_polygon(data = KD.eachID.pre.night$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 0.3) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.14, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.595, 32.645))
plot(p.KDE.pre.day.night)

if (save.fig)
  ggsave(plot = p.KDE.pre.day.night,
         filename = "figures/KDE_pre_day_night.png",
         device = "png",
         dpi = 600)

```

Post period and daytime. 

```{r}


p.KDE.post.day <- ggplot() + 
  geom_polygon(data = KD.eachID.post.day$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 1.0) +

  geom_polygon(data = KD.eachID.post.day$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 1.0) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.14, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.595, 32.655))

if (save.fig)
  ggsave(plot = p.KDE.post.day,
         filename = "figures/KDE_post_day.png",
         device = "png",
         dpi = 600)

plot(p.KDE.post.day)

```

Post period night time overlayed on top of daytime. 

```{r}


p.KDE.post.day.night <- ggplot() + 
     geom_polygon(data = KD.eachID.post.day$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightcyan",
               alpha = 1.0) +
  # geom_polygon(data = KD.eachID.post.day$vert.75.df,
  #              aes(x = long, y = lat,
  #                  group = group),
  #              color = "black",
  #              fill = "deepskyblue",
  #              alpha = 0.7) +
  
  geom_polygon(data = KD.eachID.post.day$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "blue4",
               alpha = 1.0) +
  geom_polygon(data = KD.eachID.post.night$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 0.3) +
  # geom_polygon(data = KD.eachID.post.night$vert.75.df,
  #              aes(x = long, y = lat,
  #                  group = group),
  #              color = "black",
  #              fill = "indianred",
  #              alpha = 0.3) +
  
  geom_polygon(data = KD.eachID.post.night$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 0.3) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 3) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.14, -117.085)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.595, 32.655))

if (save.fig)
  ggsave(plot = p.KDE.post.day.night,
         filename = "figures/KDE_post_day_night.png",
         device = "png",
         dpi = 600)

plot(p.KDE.post.day.night)
```


Combine all turtles together - day and night. 


```{r}
p.KDE.pre.all <- ggplot() + 
  geom_polygon(data = UD.pre.95.latlon,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightgoldenrod1",
               alpha = 1.0) +
  geom_polygon(data = UD.pre.50.latlon,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "gold",
               alpha = 1.0) +
  
  coord_map() + 
  # facet_grid(. ~ ID) +
  # facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.14, -117.08)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.60, 32.64))

if (save.fig)
  ggsave(plot = p.KDE.post.day.night,
         filename = "figures/KDE_pre_all.png",
         device = "png",
         dpi = 600)

plot(p.KDE.pre.all)
```


```{r}

p.KDE.pre.post.all <- ggplot() + 
  geom_polygon(data = UD.pre.95.latlon,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightgoldenrod1",
               alpha = 1.0) +
  geom_polygon(data = UD.pre.50.latlon,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "gold",
               alpha = 1.0) +
     geom_polygon(data = UD.post.95.latlon,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightgreen",
               alpha = 0.4) +
  geom_polygon(data = UD.post.50.latlon,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "green1",
               alpha = 0.4) +
  
  coord_map() + 
  # facet_grid(. ~ ID) +
  # facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.14, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.60, 32.65))

if (save.fig)
  ggsave(plot = p.KDE.post.day.night,
         filename = "figures/KDE_pre_post_all.png",
         device = "png",
         dpi = 600)

plot(p.KDE.pre.post.all)
```

Then split these into day and night.


Plot pre night vs day
```{r}

p.KDE.pre.DayVsNight <- ggplot() + 
  geom_polygon(data = UD.pre.day.night.95.latlon,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightgoldenrod1",
               alpha = 1.0) +
  geom_polygon(data = UD.pre.day.night.50.latlon,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "gold",
               alpha = 1.0) +
  coord_map() + 
  facet_grid(. ~ daynight) +
  # facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.14, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.60, 32.64))

if (save.fig)
  ggsave(plot = p.KDE.pre.DayVsNight,
         filename = "figures/KDE_pre_all_DayVsNight.png",
         device = "png",
         dpi = 600)

plot(p.KDE.pre.DayVsNight)
```




Plot post night vs day
```{r}


p.KDE.post.DayVsNight <- ggplot() + 
  geom_polygon(data = UD.post.day.night.95.latlon,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightgreen",
               alpha = 1.0) +
  geom_polygon(data = UD.post.day.night.50.latlon,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "green1",
               alpha = 1.0) +
  coord_map() + 
  facet_grid(. ~ daynight) +
  # facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.14, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.60, 32.65))

if (save.fig)
  ggsave(plot = p.KDE.post.DayVsNight,
         filename = "figures/KDE_post_all_DayVsNight.png",
         device = "png",
         dpi = 600)

plot(p.KDE.post.DayVsNight)
```


```{r}
UD.pre.day.night.50.latlon$period <- "pre"
UD.pre.day.night.95.latlon$period <- "pre"
UD.post.day.night.50.latlon$period <- "post"
UD.post.day.night.95.latlon$period <- "post"

UD.pre.post.day.night.50 <- rbind(UD.pre.day.night.50.latlon,
                                  UD.post.day.night.50.latlon)
UD.pre.post.day.night.95 <- rbind(UD.pre.day.night.95.latlon,
                                  UD.post.day.night.95.latlon)

UD.pre.post.day.night.50$daynight.f <- factor(UD.pre.post.day.night.50$daynight,
                                              levels = c("day", "night"))

UD.pre.post.day.night.95$daynight.f <- factor(UD.pre.post.day.night.95$daynight,
                                              levels = c("day", "night"))

UD.pre.post.day.night.50$period.f <- factor(UD.pre.post.day.night.50$period,
                                              levels = c("pre", "post"))

UD.pre.post.day.night.95$period.f <- factor(UD.pre.post.day.night.95$period,
                                              levels = c("pre", "post"))

p.KDE.pre.post.DayVsNight <- ggplot() + 
  geom_polygon(data = UD.pre.post.day.night.95,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightgoldenrod1",
               alpha = 1.0) +
  geom_polygon(data = UD.pre.post.day.night.50,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "gold",
               alpha = 1.0) +
  
  geom_polygon(data = UD.pre.post.day.night.95,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightgreen",
               alpha = 0.4) +
  geom_polygon(data = UD.pre.post.day.night.50,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "green1",
               alpha = 0.4) +
  
  coord_map() + 
  facet_grid(daynight.f ~ period.f) +
  # facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.13, -117.11, -117.09),
                     limits = c(-117.13, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.60, 32.65))

if (save.fig)
  ggsave(plot = p.KDE.pre.post.DayVsNight,
         filename = "figures/KDE_all_preVspost_DayVsNight.png",
         device = "png",
         dpi = 600)

plot(p.KDE.pre.post.DayVsNight)
```



