---
title: "Compare pre vs. post periods"
output: html_notebook
---

Extract UDs for pre/post/day/night combinations. Also for each individual and combined together. Results of this analysis are saved and used in plot_PreVsPostAnalylsis_DayNight.Rmd to make plots. Updated for the ms revision in Dec 2019.

```{r message=FALSE}
rm(list = ls())

ifelse(Sys.info()[1] == 'Linux',
       source('~/Documents/R/tools/TomosFunctions.R'),
       source('~/R/tools/TomosFunctions.R'))

#library(readxl)
library(dplyr)
library(adehabitatHR)
library(rgdal)
library(leaflet) 
library(ggplot2)
library(lubridate)
library(tidyverse)
library(ggridges)

source("HR_analysis_fcns.R")

# internet <- F #TRUE
save.fig <- T

# Minimum number of relocations per individual to be included in HR analysis
min_n <- 50
#N.end <- 32.69   # approx Coronado bridge
N.end <- 32.66 # changed from 32.69 because 152314 had a gap in data points between ~32.65 and ~32.66 - seems like there was a different behavior south and north of 32.66

grid <- 1000
extent <- 1

#source("HR_analysis_fcns.R")
tagprj <- readOGR(dsn = "Tag_065_UTMzone11n", 
                  layer = "tag_065_project")
tagproj <- proj4string(tagprj)

```

Load results from HR_analysis_GPS_LC_newtags_2019-10-31.Rmd. The following files contain raw data for pre period. First, look at each turtle for day and night combined. 


```{r, message=FALSE}
pre.all <- read.csv("data/Pre_GPS_all.csv")

# first combined for pre
pre.combined.kd <- HR.analysis.step1(min_n, pre.all, 
                                     tagproj, grid = grid)

# best h is computed for each ID in UD.eachID
UD.eachID.pre.combined <- UD.eachID(pre.combined.kd)

```

Next, post period data are loaded and UDs for day and night combined are computed.
```{r, message=FALSE}
post.all <- read.csv("data/Post_GPS_all.csv")

# first combined for pre
post.combined.kd <- HR.analysis.step1(min_n, post.all, 
                                      tagproj, grid = grid)

# best h is computed for each ID in UD.eachID
UD.eachID.post.combined <- UD.eachID(post.combined.kd)

```


We then pull out just daytime for the pre period. One turtle cannot be analyzed because there were not enough relocation points in the day time. 
```{r message=FALSE}

# pre and day time
pre.all %>% filter(day1night2 == 1) -> pre.day
pre.day.kd <- HR.analysis.step1(min_n, 
                                pre.day, 
                                tagproj, 
                                grid = grid)

# best h is computed for each ID in UD.eachID
UD.eachID.pre.day <- UD.eachID(pre.day.kd)

```

Do the same for the nighttime for the pre period.

```{r message=FALSE}
# pre and night time
pre.all %>% filter(day1night2 == 2) -> pre.night
pre.night.kd <- HR.analysis.step1(min_n, 
                                  pre.night, 
                                  tagproj, 
                                  grid = grid)

# best h is computed for each ID in UD.eachID
UD.eachID.pre.night <- UD.eachID(pre.night.kd)

```

Post period and daytime. 

```{r message=FALSE}
# post and day time
post.all %>% filter(day1night2 == 1) -> post.day
post.day.kd <- HR.analysis.step1(min_n, 
                                 post.day, 
                                 tagproj, 
                                 grid = grid)

# best h is computed for each ID in UD.eachID
UD.eachID.post.day <- UD.eachID(post.day.kd)

```

Post period nighttime.

```{r message=FALSE}
# post and night
post.all %>% filter(day1night2 == 2) -> post.night
post.night.kd <- HR.analysis.step1(min_n, post.night, tagproj, grid = grid)

# best h is computed for each ID in UD.eachID
UD.eachID.post.night <- UD.eachID(post.night.kd)

```


Combine all turtles together - day and night. 
```{r message=FALSE}
pre.kd <- HR.analysis.step1(min_n, 
                            pre.all, 
                            tagproj, 
                            grid = grid)

post.kd <- HR.analysis.step1(min_n, 
                             post.all, 
                             tagproj, 
                             grid = grid)

# find the best h for all individuals combined
h.pre.1 <- find.h.adhoc(pre.kd$list.data$all.utm)
h.pre <- ceiling(h.pre.1$h)
UD.pre <- kernelUD(pre.kd$list.data$all.utm, 
                   h = h.pre, 
                   kern = "bivnorm", 
                   grid = grid)

UD.pre.95 <- getverticeshr(UD.pre, 95)
UD.pre.50 <- getverticeshr(UD.pre, 50)
    
UD.pre.95.latlon <- broom::tidy(spTransform(UD.pre.95, 
                                            CRS("+proj=longlat")))
UD.pre.50.latlon <- broom::tidy(spTransform(UD.pre.50, 
                                            CRS("+proj=longlat")))

# work on the post period
h.post.1 <- find.h.adhoc(post.kd$list.data$all.utm)

h.post <- ceiling(h.post.1$h)

UD.post <- kernelUD(post.kd$list.data$all.utm, 
                    h = h.post, 
                    kern = "bivnorm", 
                    grid = grid)

UD.post.95 <- getverticeshr(UD.post, 95)
UD.post.50 <- getverticeshr(UD.post, 50)
    
UD.post.95.latlon <- broom::tidy(spTransform(UD.post.95, 
                                             CRS("+proj=longlat")))
UD.post.50.latlon <- broom::tidy(spTransform(UD.post.50, 
                                             CRS("+proj=longlat")))


```


Then compute UDs separatrely for day and night.

```{r message=FALSE}
h.pre.1 <- find.h.adhoc(pre.day.kd$list.data$all.utm)
h.pre.day <- ceiling(h.pre.1$h)

UD.pre.day <- kernelUD(pre.day.kd$list.data$all.utm, 
                       h = h.pre.day, 
                       kern = "bivnorm", 
                       grid = grid)

UD.pre.day.95 <- getverticeshr(UD.pre.day, 95)
UD.pre.day.50 <- getverticeshr(UD.pre.day, 50)
    
UD.pre.day.95.latlon <- broom::tidy(spTransform(UD.pre.day.95,
                                                CRS("+proj=longlat")))
UD.pre.day.95.latlon$daynight <- "day"
UD.pre.day.50.latlon <- broom::tidy(spTransform(UD.pre.day.50,
                                                CRS("+proj=longlat")))
UD.pre.day.50.latlon$daynight <- "day"

h.pre.1 <- find.h.adhoc(pre.night.kd$list.data$all.utm)
h.pre.night <- ceiling(h.pre.1$h)

UD.pre.night <- kernelUD(pre.night.kd$list.data$all.utm, 
                         h = h.pre.night, 
                         kern = "bivnorm", 
                         grid = grid)

UD.pre.night.95 <- getverticeshr(UD.pre.night, 95)
UD.pre.night.50 <- getverticeshr(UD.pre.night, 50)
    
UD.pre.night.95.latlon <- broom::tidy(spTransform(UD.pre.night.95,
                                                  CRS("+proj=longlat")))
UD.pre.night.95.latlon$daynight <- "night"
UD.pre.night.50.latlon <- broom::tidy(spTransform(UD.pre.night.50,
                                                  CRS("+proj=longlat")))
UD.pre.night.50.latlon$daynight <- "night"

UD.pre.day.night.95.latlon <- rbind(UD.pre.day.95.latlon, 
                                    UD.pre.night.95.latlon)
UD.pre.day.night.50.latlon <- rbind(UD.pre.day.50.latlon, 
                                    UD.pre.night.50.latlon)
```

For the post period

```{r message=FALSE}
h.post.1 <- find.h.adhoc(post.day.kd$list.data$all.utm)
h.post.day <- ceiling(h.post.1$h)

UD.post.day <- kernelUD(post.day.kd$list.data$all.utm, 
                        h = h.post.day, 
                        kern = "bivnorm", 
                        grid = grid)

UD.post.day.95 <- getverticeshr(UD.post.day, 95)
UD.post.day.50 <- getverticeshr(UD.post.day, 50)
    
UD.post.day.95.latlon <- broom::tidy(spTransform(UD.post.day.95,
                                                 CRS("+proj=longlat")))
UD.post.day.95.latlon$daynight <- "day"
UD.post.day.50.latlon <- broom::tidy(spTransform(UD.post.day.50,
                                                 CRS("+proj=longlat")))
UD.post.day.50.latlon$daynight <- "day"

h.post.1 <- find.h.adhoc(post.night.kd$list.data$all.utm)
h.post.night <- ceiling(h.post.1$h)

UD.post.night <- kernelUD(post.night.kd$list.data$all.utm, 
                          h = h.post.night, 
                          kern = "bivnorm", 
                          grid = grid)

UD.post.night.95 <- getverticeshr(UD.post.night, 95)
UD.post.night.50 <- getverticeshr(UD.post.night, 50)
    
UD.post.night.95.latlon <- broom::tidy(spTransform(UD.post.night.95,
                                                   CRS("+proj=longlat")))
UD.post.night.95.latlon$daynight <- "night"
UD.post.night.50.latlon <- broom::tidy(spTransform(UD.post.night.50,
                                                   CRS("+proj=longlat")))
UD.post.night.50.latlon$daynight <- "night"


UD.post.day.night.95.latlon <- rbind(UD.post.day.95.latlon, 
                                     UD.post.night.95.latlon)
UD.post.day.night.50.latlon <- rbind(UD.post.day.50.latlon, 
                                     UD.post.night.50.latlon)
```


Save results. 

```{r message=FALSE}
#These are the only things needed for making plots
save.list <- list(UD.eachID.pre.daynight = UD.eachID.pre.combined, 
                  UD.eachID.post.daynight = UD.eachID.post.combined,
                  UD.eachID.pre.day = UD.eachID.pre.day, 
                  UD.eachID.pre.night = UD.eachID.pre.night, 
                  UD.eachID.post.day = UD.eachID.post.day, 
                  UD.eachID.post.night = UD.eachID.post.night, 
                  UD95.allID.post.daynight = UD.post.95.latlon, 
                  UD50.allID.post.daynight = UD.post.50.latlon, 
                  UD95.allID.pre.daynight = UD.pre.95.latlon, 
                  UD50.allID.pre.daynight = UD.pre.50.latlon, 
                  UD95.allID.pre.day = UD.pre.day.95.latlon, 
                  UD50.allID.pre.day = UD.pre.day.50.latlon,
                  UD95.allID.pre.night = UD.pre.night.95.latlon, 
                  UD50.allID.pre.night = UD.pre.night.50.latlon, 
                  UD95.allID.post.day = UD.post.day.95.latlon,
                  UD50.allID.post.day = UD.post.day.50.latlon, 
                  UD95.allID.post.night = UD.post.night.95.latlon, 
                  UD50.allID.post.night = UD.post.night.50.latlon,
                  UD95.allID.pre.day.night = UD.pre.day.night.95.latlon, 
                  UD50.allID.pre.day.night = UD.pre.day.night.50.latlon,
                  UD95.allID.post.day.night = UD.post.day.night.95.latlon, 
                  UD50.allID.post.day.night = UD.post.day.night.50.latlon)

saveRDS(save.list, file = "RData/PreVsPost_DayNight_Dec2019.RDS")

```

