---
title: "Compare pre vs. post periods"
output: html_notebook
---

This file contains code to compare pre and post periods by randomly extracting the same number of individuals as the pre period from the post period without replacement and compare the calculated HR areas. It also looks at the northern most latitude of 95% and 50% UDs.

```{r message=FALSE}
rm(list = ls())

ifelse(Sys.info()[1] == 'Linux',
       source('~/Documents/R/tools/TomosFunctions.R'),
       source('~/R/tools/TomosFunctions.R'))

#library(readxl)
library(dplyr)
library(adehabitatHR)
library(rgdal)
library(leaflet) 
library(ggplot2)
library(lubridate)
library(tidyverse)
library(ggridges)

source("HR_analysis_fcns.R")

# internet <- F #TRUE
save.fig <- T

# Minimum number of relocations per individual to be included in HR analysis
min_n <- 50
#N.end <- 32.69   # approx Coronado bridge
N.end <- 32.66 # changed from 32.69 because 152314 had a gap in data points between ~32.65 and ~32.66 - seems like there was a different behavior south and north of 32.66

grid <- 1000
extent <- 1


source("HR_analysis_fcns.R")
tagprj <- readOGR(dsn = "Tag_065_UTMzone11n", 
                  layer = "tag_065_project")
tagproj <- proj4string(tagprj)

```

Load results from HR_analysis_GPS_LC_newtags_11July2018.Rmd. The following files contain raw data for pre period. First, look at each turtle for day and night combined. 

```{r, message=FALSE}
pre.all <- read.csv("data/Pre_GPS_LC_all_2018-09-18.csv")

# first combined for pre
pre.combined.kd <- HR.analysis.step1(min_n, pre.all, tagproj, grid = grid)
#h.pre.combined.1 <- find.h.adhoc(pre.combined.kd$list.data$all.utm)
#h.pre.combined <- round(h.pre.day.1$h)
KD.eachID.pre.combined <- UD.eachID(pre.combined.kd)


```


Next, post period data are loaded and UDs for day and night combined are computed.
```{r, message=FALSE}
post.all <- read.csv("data/Post_GPS_LC_all_2018-09-18.csv")

# first combined for pre
post.combined.kd <- HR.analysis.step1(min_n, post.all, tagproj, grid = grid)
#h.pre.combined.1 <- find.h.adhoc(pre.combined.kd$list.data$all.utm)
#h.pre.combined <- round(h.pre.day.1$h)
KD.eachID.post.combined <- UD.eachID(post.combined.kd)


```


We then pull out just day time for the pre period. One turtle cannot be analyzed because there were not enough relocation points in the day time. 
```{r message=FALSE}

# pre and day time
pre.all %>% filter(day1night2 == 1) -> pre.day
pre.day.kd <- HR.analysis.step1(min_n, pre.day, tagproj, grid = grid)
# h.pre.day.1 <- find.h.adhoc(pre.day.kd$list.data$all.utm)
# h.pre.day <- round(h.pre.day.1$h)

# compute.area also provides areas for each individuals separately,
# they will be different from that computed by UD.eachID because h values
# are different in the latter - optimized for each individual. 
#pre.day.HR <- compute.area(h.pre.day, 
#                           pre.day.kd$list.data)

KD.eachID.pre.day <- UD.eachID(pre.day.kd)

```

Do the same for the nighttime for the pre period and plot on top of the daytime UDs.

```{r message=FALSE}
# pre and night time
pre.all %>% filter(day1night2 == 2) -> pre.night
pre.night.kd <- HR.analysis.step1(min_n, pre.night, tagproj, grid = grid)
# h.pre.night.1 <- find.h.adhoc(pre.night.kd$list.data$all.utm)
# h.pre.night <- round(h.pre.night.1$h)
# pre.night.HR <- compute.area(h.pre.night, pre.night.kd$list.data)
KD.eachID.pre.night <- UD.eachID(pre.night.kd)

```

Post period and daytime. 

```{r message=FALSE}
# post and day time
post.all %>% filter(day1night2 == 1) -> post.day
post.day.kd <- HR.analysis.step1(min_n, post.day, tagproj, grid = grid)
# h.post.day.1 <- find.h.adhoc(post.day.kd$list.data$all.utm)
# h.post.day <- round(h.post.day.1$h)
# post.day.HR <- compute.area(h.post.day, post.day.kd$list.data)
KD.eachID.post.day <- UD.eachID(post.day.kd)


```

Post period night time overlayed on top of daytime. 

```{r message=FALSE}
# post and night
post.all %>% filter(day1night2 == 2) -> post.night
post.night.kd <- HR.analysis.step1(min_n, post.night, tagproj, grid = grid)
# h.post.night.1 <- find.h.adhoc(post.night.kd$list.data$all.utm)
# h.post.night <- round(h.post.night.1$h)
# post.night.HR <- compute.area(h.post.night, post.night.kd$list.data)
KD.eachID.post.night <- UD.eachID(post.night.kd)


```


Combine all turtles together - day and night. 
```{r message=FALSE}
pre.kd <- HR.analysis.step1(min_n, pre.all, tagproj, grid = grid)
post.kd <- HR.analysis.step1(min_n, post.all, tagproj, grid = grid)

h.pre.1 <- find.h.adhoc(pre.kd$list.data$all.utm)
h.pre <- round(h.pre.1$h)

UD.pre <- kernelUD(pre.kd$list.data$all.utm, 
                   h = h.pre, 
                   kern = "bivnorm", 
                   grid = grid)

# UD.pre.tmp <- kernel.area(UD.pre,
#                           percent = c(50, 95),
#                           unin = c("m"),
#                           unout = c("km2"),
#                           standardize = FALSE)
    
UD.pre.95 <- getverticeshr(UD.pre, 95)
UD.pre.50 <- getverticeshr(UD.pre, 50)
    
UD.pre.95.latlon <- broom::tidy(spTransform(UD.pre.95, CRS("+proj=longlat")))
UD.pre.50.latlon <- broom::tidy(spTransform(UD.pre.50, CRS("+proj=longlat")))

# work on the post period
h.post.1 <- find.h.adhoc(post.kd$list.data$all.utm)

h.post <- round(h.post.1$h)

UD.post <- kernelUD(post.kd$list.data$all.utm, 
                    h = h.post, 
                    kern = "bivnorm", 
                    grid = grid)

# UD.post.tmp <- kernel.area(UD.post,
#                            percent = c(50, 95),
#                            unin = c("m"),
#                            unout = c("km2"),
#                            standardize = FALSE)

UD.post.95 <- getverticeshr(UD.post, 95)
UD.post.50 <- getverticeshr(UD.post, 50)
    
UD.post.95.latlon <- broom::tidy(spTransform(UD.post.95, CRS("+proj=longlat")))
UD.post.50.latlon <- broom::tidy(spTransform(UD.post.50, CRS("+proj=longlat")))


```



Then split these into day and night.

```{r message=FALSE}
h.pre.1 <- find.h.adhoc(pre.day.kd$list.data$all.utm)
h.pre.day <- round(h.pre.1$h)

UD.pre.day <- kernelUD(pre.day.kd$list.data$all.utm, 
                   h = h.pre.day, 
                   kern = "bivnorm", 
                   grid = grid)

# UD.pre.tmp <- kernel.area(UD.pre,
#                           percent = c(50, 95),
#                           unin = c("m"),
#                           unout = c("km2"),
#                           standardize = FALSE)
    
UD.pre.day.95 <- getverticeshr(UD.pre.day, 95)
UD.pre.day.50 <- getverticeshr(UD.pre.day, 50)
    
UD.pre.day.95.latlon <- broom::tidy(spTransform(UD.pre.day.95, CRS("+proj=longlat")))
UD.pre.day.95.latlon$daynight <- "day"
UD.pre.day.50.latlon <- broom::tidy(spTransform(UD.pre.day.50, CRS("+proj=longlat")))
UD.pre.day.50.latlon$daynight <- "day"


h.pre.1 <- find.h.adhoc(pre.night.kd$list.data$all.utm)
h.pre.night <- round(h.pre.1$h)

UD.pre.night <- kernelUD(pre.night.kd$list.data$all.utm, 
                   h = h.pre.night, 
                   kern = "bivnorm", 
                   grid = grid)

# UD.pre.tmp <- kernel.area(UD.pre,
#                           percent = c(50, 95),
#                           unin = c("m"),
#                           unout = c("km2"),
#                           standardize = FALSE)
    
UD.pre.night.95 <- getverticeshr(UD.pre.night, 95)
UD.pre.night.50 <- getverticeshr(UD.pre.night, 50)
    
UD.pre.night.95.latlon <- broom::tidy(spTransform(UD.pre.night.95, CRS("+proj=longlat")))
UD.pre.night.95.latlon$daynight <- "night"
UD.pre.night.50.latlon <- broom::tidy(spTransform(UD.pre.night.50, CRS("+proj=longlat")))
UD.pre.night.50.latlon$daynight <- "night"

UD.pre.day.night.95.latlon <- rbind(UD.pre.day.95.latlon, UD.pre.night.95.latlon)
UD.pre.day.night.50.latlon <- rbind(UD.pre.day.50.latlon, UD.pre.night.50.latlon)
```




```{r message=FALSE}
h.post.1 <- find.h.adhoc(post.day.kd$list.data$all.utm)
h.post.day <- round(h.post.1$h)

UD.post.day <- kernelUD(post.day.kd$list.data$all.utm, 
                   h = h.post.day, 
                   kern = "bivnorm", 
                   grid = grid)

# UD.pre.tmp <- kernel.area(UD.pre,
#                           percent = c(50, 95),
#                           unin = c("m"),
#                           unout = c("km2"),
#                           standardize = FALSE)
    
UD.post.day.95 <- getverticeshr(UD.post.day, 95)
UD.post.day.50 <- getverticeshr(UD.post.day, 50)
    
UD.post.day.95.latlon <- broom::tidy(spTransform(UD.post.day.95, CRS("+proj=longlat")))
UD.post.day.95.latlon$daynight <- "day"
UD.post.day.50.latlon <- broom::tidy(spTransform(UD.post.day.50, CRS("+proj=longlat")))
UD.post.day.50.latlon$daynight <- "day"


h.post.1 <- find.h.adhoc(post.night.kd$list.data$all.utm)
h.post.night <- round(h.post.1$h)

UD.post.night <- kernelUD(post.night.kd$list.data$all.utm, 
                   h = h.post.night, 
                   kern = "bivnorm", 
                   grid = grid)

# UD.pre.tmp <- kernel.area(UD.pre,
#                           percent = c(50, 95),
#                           unin = c("m"),
#                           unout = c("km2"),
#                           standardize = FALSE)
    
UD.post.night.95 <- getverticeshr(UD.post.night, 95)
UD.post.night.50 <- getverticeshr(UD.post.night, 50)
    
UD.post.night.95.latlon <- broom::tidy(spTransform(UD.post.night.95, CRS("+proj=longlat")))
UD.post.night.95.latlon$daynight <- "night"
UD.post.night.50.latlon <- broom::tidy(spTransform(UD.post.night.50, CRS("+proj=longlat")))
UD.post.night.50.latlon$daynight <- "night"


UD.post.day.night.95.latlon <- rbind(UD.post.day.95.latlon, UD.post.night.95.latlon)
UD.post.day.night.50.latlon <- rbind(UD.post.day.50.latlon, UD.post.night.50.latlon)
```


Save results. 

```{r message=FALSE}
#These are the only things needed for making plots
save.list <- list(KD.eachID.pre.combined, KD.eachID.post.combined, KD.eachID.pre.day, 
                  KD.eachID.pre.night, KD.eachID.post.day, KD.eachID.post.night, 
                  UD.post.95.latlon, UD.post.50.latlon, UD.pre.95.latlon, 
                  UD.pre.50.latlon, UD.pre.day.95.latlon, UD.pre.day.50.latlon,
                  UD.pre.night.95.latlon, UD.pre.night.50.latlon, UD.post.day.95.latlon,
                  UD.post.day.50.latlon, UD.post.night.95.latlon, UD.post.night.50.latlon,
                  UD.pre.day.night.95.latlon, UD.pre.day.night.50.latlon,
                  UD.post.day.night.95.latlon, UD.post.day.night.50.latlon)

saveRDS(save.list, file = "RData/PreVsPost_DayNight.RDS")

```

