---
title: "Compare pre vs. post periods"
output: html_notebook
---

This file contains code to compare pre and post periods by randomly extracting the same number of individuals as the pre period from the post period without replacement and compare the calculated HR areas. It also looks at the northern most latitude of 95% and 50% UDs.

```{r}
rm(list = ls())

ifelse(Sys.info()[1] == 'Linux',
       source('~/Documents/R/tools/TomosFunctions.R'),
       source('~/R/tools/TomosFunctions.R'))

#library(readxl)
library(dplyr)
library(adehabitatHR)
library(rgdal)
library(leaflet) 
library(ggplot2)
library(lubridate)
library(tidyverse)
library(ggridges)

source("HR_analysis_fcns.R")

# internet <- F #TRUE
save.fig <- T

# Minimum number of relocations per individual to be included in HR analysis
min_n <- 50
#N.end <- 32.69   # approx Coronado bridge
N.end <- 32.66 # changed from 32.69 because 152314 had a gap in data points between ~32.65 and ~32.66 - seems like there was a different behavior south and north of 32.66

grid <- 1000
extent <- 1


source("HR_analysis_fcns.R")
tagprj <- readOGR(dsn = "Tag_065_UTMzone11n", 
                  layer = "tag_065_project")
tagproj <- proj4string(tagprj)

```

Load results from HR_analysis_GPS_LC_newtags_11July2018.Rmd. The following files contain raw data for pre and post periods. Analyze day vs nights here. 

```{r, message=FALSE}
pre.all <- read.csv("data/Pre_GPS_LC_all_2018-09-18.csv")

# first combined for pre
pre.combined.kd <- HR.analysis.step1(min_n, pre.all, tagproj, grid = grid)
#h.pre.combined.1 <- find.h.adhoc(pre.combined.kd$list.data$all.utm)
#h.pre.combined <- round(h.pre.day.1$h)
KD.eachID.pre.combined <- UD.eachID(pre.combined.kd)

p.KDE.pre.combined <- ggplot() + 
  geom_polygon(data = KD.eachID.pre.combined$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 0.7) +

  geom_polygon(data = KD.eachID.pre.combined$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 0.4) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65))
plot(p.KDE.pre.combined)

if (save.fig)
  ggsave(plot = p.KDE.pre.combined,
         filename = "figures/KDE_pre_combined.png",
         device = "png",
         dpi = 600)
```



```{r, message=FALSE}
post.all <- read.csv("data/Post_GPS_LC_all_2018-09-18.csv")

# first combined for pre
post.combined.kd <- HR.analysis.step1(min_n, post.all, tagproj, grid = grid)
#h.pre.combined.1 <- find.h.adhoc(pre.combined.kd$list.data$all.utm)
#h.pre.combined <- round(h.pre.day.1$h)
KD.eachID.post.combined <- UD.eachID(post.combined.kd)

p.KDE.post.combined <- ggplot() + 
  geom_polygon(data = KD.eachID.post.combined$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 0.7) +

  geom_polygon(data = KD.eachID.post.combined$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 0.4) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 3) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.08)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.66))
plot(p.KDE.post.combined)

if (save.fig)
  ggsave(plot = p.KDE.post.combined,
         filename = "figures/KDE_post_combined.png",
         device = "png",
         dpi = 600)
```



```{r}

# pre and day time
pre.all %>% filter(day1night2 == 1) -> pre.day
pre.day.kd <- HR.analysis.step1(min_n, pre.day, tagproj, grid = grid)
# h.pre.day.1 <- find.h.adhoc(pre.day.kd$list.data$all.utm)
# h.pre.day <- round(h.pre.day.1$h)

# compute.area also provides areas for each individuals separately,
# they will be different from that computed by UD.eachID because h values
# are different in the latter - optimized for each individual. 
#pre.day.HR <- compute.area(h.pre.day, 
#                           pre.day.kd$list.data)

KD.eachID.pre.day <- UD.eachID(pre.day.kd)

p.KDE.pre.day <- ggplot() + 
  geom_polygon(data = KD.eachID.pre.day$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 0.7) +

  geom_polygon(data = KD.eachID.pre.day$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 0.4) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65))
plot(p.KDE.pre.day)

if (save.fig)
  ggsave(plot = p.KDE.pre.day,
         filename = "figures/KDE_pre_day.png",
         device = "png",
         dpi = 600)

```



```{r}
# pre and night time
pre.all %>% filter(day1night2 == 2) -> pre.night
pre.night.kd <- HR.analysis.step1(min_n, pre.night, tagproj, grid = grid)
# h.pre.night.1 <- find.h.adhoc(pre.night.kd$list.data$all.utm)
# h.pre.night <- round(h.pre.night.1$h)
# pre.night.HR <- compute.area(h.pre.night, pre.night.kd$list.data)
KD.eachID.pre.night <- UD.eachID(pre.night.kd)

p.KDE.pre.day.night <- ggplot() + 
    geom_polygon(data = KD.eachID.pre.day$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightcyan",
               alpha = 0.7) +

  geom_polygon(data = KD.eachID.pre.day$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "blue4",
               alpha = 0.7) +

  geom_polygon(data = KD.eachID.pre.night$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 0.3) +

  geom_polygon(data = KD.eachID.pre.night$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 0.3) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.65))
plot(p.KDE.pre.day.night)

if (save.fig)
  ggsave(plot = p.KDE.pre.day.night,
         filename = "figures/KDE_pre_day_night.png",
         device = "png",
         dpi = 600)

```

```{r}
# post and day time
post.all %>% filter(day1night2 == 1) -> post.day
post.day.kd <- HR.analysis.step1(min_n, post.day, tagproj, grid = grid)
# h.post.day.1 <- find.h.adhoc(post.day.kd$list.data$all.utm)
# h.post.day <- round(h.post.day.1$h)
# post.day.HR <- compute.area(h.post.day, post.day.kd$list.data)
KD.eachID.post.day <- UD.eachID(post.day.kd)

p.KDE.post.day <- ggplot() + 
  geom_polygon(data = KD.eachID.post.day$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 0.7) +

  geom_polygon(data = KD.eachID.post.day$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 0.4) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.09)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.66))

if (save.fig)
  ggsave(plot = p.KDE.post.day,
         filename = "figures/KDE_post_day.png",
         device = "png",
         dpi = 600)

plot(p.KDE.post.day)

```



```{r}
# post and night
post.all %>% filter(day1night2 == 2) -> post.night
post.night.kd <- HR.analysis.step1(min_n, post.night, tagproj, grid = grid)
# h.post.night.1 <- find.h.adhoc(post.night.kd$list.data$all.utm)
# h.post.night <- round(h.post.night.1$h)
# post.night.HR <- compute.area(h.post.night, post.night.kd$list.data)
KD.eachID.post.night <- UD.eachID(post.night.kd)


p.KDE.post.day.night <- ggplot() + 
     geom_polygon(data = KD.eachID.post.day$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightcyan",
               alpha = 0.7) +
  # geom_polygon(data = KD.eachID.post.day$vert.75.df,
  #              aes(x = long, y = lat,
  #                  group = group),
  #              color = "black",
  #              fill = "deepskyblue",
  #              alpha = 0.7) +
  
  geom_polygon(data = KD.eachID.post.day$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "blue4",
               alpha = 0.7) +
  geom_polygon(data = KD.eachID.post.night$vert.95.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "lightpink",
               alpha = 0.3) +
  # geom_polygon(data = KD.eachID.post.night$vert.75.df,
  #              aes(x = long, y = lat,
  #                  group = group),
  #              color = "black",
  #              fill = "indianred",
  #              alpha = 0.3) +
  
  geom_polygon(data = KD.eachID.post.night$vert.50.df,
               aes(x = long, y = lat,
                   group = group),
               color = "black",
               fill = "red4",
               alpha = 0.3) +
  coord_map() + 
  facet_grid(. ~ ID) +
  facet_wrap( ~ ID, nrow = 2) + 
  labs(x = "", y = "")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  scale_x_continuous(breaks = c(-117.14, -117.12, -117.10),
                     limits = c(-117.15, -117.08)) +
  scale_y_continuous(breaks = c(32.60, 32.62, 32.64),
                     limits = c(32.59, 32.66))

if (save.fig)
  ggsave(plot = p.KDE.post.day.night,
         filename = "figures/KDE_post_day_night.png",
         device = "png",
         dpi = 600)

plot(p.KDE.post.day.night)
```




