---
title: "Request by Mike Zickel (Navy) on 2021-12-08"
output: html_notebook
---


```{r message=FALSE}
rm(list = ls())

library(tidyverse)
library(adehabitatHR)
```

Mike Zickel requested shapefiles for the homeranges that we estimated in Eguchi et al. (2020). 

"Hi Jeff,

Thank you for sending the thesis. Very helpful!

I have another request. Would it be possible to get the shapefiles for the home ranges of green turtles in San Diego Bay shown in Eguchi et al. (2020)?

I would like to use the 95% range as the area for estimating a density in the south part of the Bay.

For reference, in our previous iteration of density estimates, we assumed 61 green turtles in the Bay, with 95% in the south Bay and 5% in the north bay in summer and fall, and then 100% in the south Bay in winter and spring (0% in the north Bay). See attached maps.

I would still assume some percentage of turtles occur in the north bay in summer and fall (5%?), but I would like to use the home ranges as the distribution area in the south Bay, unless you think that would not be appropriate.

Eguchi, T., J. Bredvik, S. Graham, R. LeRoux, B. Saunders, and J. A. Seminoff. (2020). Effects of a power plant closure on home ranges of green turtles in an urban foraging area. Endangered Species Research, 41, 265-277.

Thanks,

Mike"

I responded that I did not make shapefiles but can provide lat-lon pairs. 

This notebook creates those files.

Get the RData file that contains all home ranges:

```{r}
# this was created in PreVsPostAnalysis_DayNight_Dec2019.Rmd
HR.all <- readRDS(file = "RData/PreVsPost_DayNight_Dec2021.rds")
set.names <- names(HR.all)

k <- 7
k1 <- 1
for (k in 1:length(set.names)){
  out.name.root <- str_replace_all(set.names[k], "[.]", "_")
  # for each item in HR.all[[k]], k < 7, there are 9 items 
  # (created by UD.eachID function in HR_analysis_fcns.R).
  # These are named. "vert.95.df" is what he's after.
  #tmp <- HR.all[[k]]$vert.95.df
  #out.name <- paste0(out.name.root, ".csv")
  #write_csv(tmp, file = paste0("data/MikeZickel_Dec2021/", out.name))
  IDs <- unique(HR.all[[k]]$vert.95.df$ID)
  if (is.null(IDs)){
    # all individuals combined together
    UD.95 <- getverticeshr(HR.all[[k]], 95, unin = "m", unout = "km2")
    raster::shapefile(UD.95,
                        paste0("data/MikeZickel_Dec2021/", 
                               out.name.root, ".shp"), 
                      overwrite = T)
  } else {
    # for each individual
    for (k1 in 1:length(HR.all[[k]]$UD.95)){    
      # Or use shapefile function in raster package to create shapefiles
      raster::shapefile(HR.all[[k]]$UD.95[[k1]],
                        paste0("data/MikeZickel_Dec2021/", 
                               out.name.root, "_", 
                               IDs[k1],  ".shp"), overwrite = T)
    }  
    
  }
  
  
  
}
```

